---
title: "LabExercise2.Rmd"
author: "Natalie Joy Loredo"
date: "2024-03-20"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Libraries
```{r}
library(rvest)
library(dplyr)
library(polite)
library(stringr) 
library(httr)
```
Scrape 5O Products, Product Name, Type of purchase, Date of review, Individual rating, and Reviews in amazon)
```{r }
#Get 24 Products in 50
products1 <- "https://www.amazon.com.au/s?bbn=4851799051&rh=n%3A6035839051&language=en_AU&_encoding=UTF8&brr=1&content-id=amzn1.sym.b8ed1d3c-2f91-48cc-baac-e6d8e7f439e4&pd_rd_r=708b8da9-4d12-4c9c-b945-e5349e7120c8&pd_rd_w=AsqeN&pd_rd_wg=r572i&pf_rd_p=b8ed1d3c-2f91-48cc-baac-e6d8e7f439e4&pf_rd_r=2EVHVJ7QKDNTJEC8HDFT&rd=1&ref=Oct_d_odnav_d_4885206051_0"

session <- bow(products1, user_agent = "Educational Purposes")
session

first24 <- read_html(products1)

#subset 24 products
firstset24<- first24%>%
    html_nodes("h2")%>%
    html_text()
firstset24

subset24products<- firstset24[1:24]
subset24products
```
Scape Another 24 Products
```{r}
#Get 24 Products in 50
products2 <- "https://www.amazon.com.au/s?i=electronics&bbn=4851799051&rh=n%3A6035839051&page=2&language=en_AU&_encoding=UTF8&brr=1&content-id=amzn1.sym.b8ed1d3c-2f91-48cc-baac-e6d8e7f439e4&pd_rd_r=708b8da9-4d12-4c9c-b945-e5349e7120c8&pd_rd_w=AsqeN&pd_rd_wg=r572i&pf_rd_p=b8ed1d3c-2f91-48cc-baac-e6d8e7f439e4&pf_rd_r=2EVHVJ7QKDNTJEC8HDFT&qid=1709397899&rd=1&ref=sr_pg_1"

session <- bow(products2, user_agent = "Educational Purposes")
session

second24 <- read_html(products2) 

#Subset Products
secondset24 <- second24%>%
    html_nodes("h2")%>%
    html_text()
secondset24

subset24products2 <- secondset24[1:24]
subset24products2
```
Scrape 2 Remaining Products
```{r}
#Get 2 Products   
products3 <- "https://www.amazon.com.au/s?i=electronics&bbn=4851799051&rh=n%3A6035839051&page=3&language=en_AU&_encoding=UTF8&brr=1&content-id=amzn1.sym.b8ed1d3c-2f91-48cc-baac-e6d8e7f439e4&pd_rd_r=708b8da9-4d12-4c9c-b945-e5349e7120c8&pd_rd_w=AsqeN&pd_rd_wg=r572i&pf_rd_p=b8ed1d3c-2f91-48cc-baac-e6d8e7f439e4&pf_rd_r=2EVHVJ7QKDNTJEC8HDFT&qid=1709398205&rd=1&ref=sr_pg_2"

session <- bow(products3, user_agent = "Educational Purposes")
session

product2 <- read_html(products3) 

#subset 2 products
last2 <- product2%>%
    html_nodes("h2")%>%
    html_text()
last2

subset2products <- last2[1:2]
subset2products
```
Combine the Products
```{r}
combinedName <- data.frame(
  ProductName = c(subset24products, subset24products2, subset2products)
)

combinedName 
```
write csv for 50 products
```{r}
write.csv(combinedName, file = "50PRODUCTS.csv") 
#load
head(combinedName)
```
First Product
```{r} 
#Get 13 Names
url1 <- "https://www.amazon.com.au/product-reviews/B0B8MQRGV8/ref=cm_cr_arp_d_viewopt_srt?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&sortBy=recent&pageNumber=1#reviews-filter-bar"
session <- bow(url1, user_agent = "Educational Purposes")
session

url_0 <- read_html(url1)  

#Get 12 Names
url1.0 <- "https://www.amazon.com.au/product-reviews/B0B8MQRGV8/ref=cm_cr_getr_d_paging_btm_next_2?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&sortBy=recent&pageNumber=2#reviews-filter-bar"
session <- bow(url1.0, user_agent = "Educational Purposes")
session

url_1 <- read_html(url1.0)

#Get 13 Names
url1.1 <- "https://www.amazon.com.au/product-reviews/B0B8MQRGV8/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&sortBy=recent&pageNumber=3#reviews-filter-bar"
session <- bow(url1.1, user_agent = "Educational Purposes")
session

url_2 <- read_html(url1.1)

#Get 12 Names
url1.2 <- "https://www.amazon.com.au/product-reviews/B0B8MQRGV8/ref=cm_cr_arp_d_paging_btm_next_4?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&sortBy=recent&pageNumber=4#reviews-filter-bar"
session <- bow(url1.2, user_agent = "Educational Purposes")
session
```
First Product
```{r}
url_3 <- read_html(url1.2)

#Get 13 Reviewer Names
names1.2 <- url_2%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names1.2 
#Get 12 Reviewer Names
names1.3 <- url_3%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names1.3

names1 <- url_0%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names1 

#Get 12 Reviewer Names 
names1.1 <- url_1%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names1.1  

names1.1 <- names1.1 [1:12]

#Get 13 Reviewer Names
names1.2 <- url_2%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names1.2 

#Get 12 Reviewer Names
names1.3 <- url_3%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names1.3

#Type of Purchase 
purchasetype1 <- url_0%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()
purchasetype1  
 
purchasetype1.1 <- url_1%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()
purchasetype1.1

purchasetype1.2<- url_2%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()
purchasetype1.2

purchasetype1.3 <- url_3%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()
purchasetype1.3

#Subset 
purchasetype1.3_ <- purchasetype1.3[1:22]

#Date of Review 
daterev1 <- url_0%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()
daterev1

daterev1.1<- url_1%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()
daterev1.1

daterev1.2<- url_2%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()
daterev1.2 

daterev1.3<- url_3%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()
daterev1.3 

#Subset
daterev1.3_ <- daterev1.3[1:20]

#Individual Ratings
rates1<- url_0%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()
rates1 

rates1.1<- url_1%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()
rates1.1

rates1.2<- url_2%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()
rates1.2 

rates1.3<- url_3%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()
rates1.3

#Review Text
reviews1 <- url_0%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>%
    gsub("\\n", "", .)
reviews1

reviews1.1 <- url_1%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>%
    gsub("\\n", "", .)
reviews1.1 

reviews1.2 <- url_2%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>%
    gsub("\\n", "", .)
reviews1.2

reviews1.3 <- url_3%>%
  html_nodes("span.a-size-base.review-text.review-text-content") %>%
  html_text() %>%
  gsub("\\n", "", .)

reviews1.3_sub <- reviews1.3[1:20]

reviews1.3_sub

#50 Product Names
title1 <- rep(subset24products[[1]],50)
title1

#Data Frames
dataname <- data.frame(
 ReviewerName = c(names1, names1.1, names1.2, names1.3)
)
dataname

#Data Frame of Type of Purchase
datapurchaseType <- data.frame(
    TypeOfPurchase = c(purchasetype1,purchasetype1.1,purchasetype1.2, purchasetype1.3_)
)
datapurchaseType

#Date of Review Data Frame
dataDate <- data.frame(
    Date = c(daterev1,daterev1.1,daterev1.2, daterev1.3_)
)
dataDate

#Individual Rating Data Frame
rate <- data.frame(
    IndividualRating = c(rates1,rates1.1,rates1.2, rates1.3)
)
rate  

#Reviews Text Data Frame
review <- data.frame(
   ReviewText = c(reviews1,reviews1.1,reviews1.2, reviews1.3_sub)
)
review 

#Selecting 50 rows from each data frame
selected_dataname <- head(dataname, 50)
selected_datapurchaseType <- head(datapurchaseType, 50)
selected_dataDate <- head(dataDate, 50)
selected_rate <- head(rate, 50)
selected_review <- head(review, 50)

#product
    pro <- rep(subset24products[1],50)

#combined dataframes
combinedProducts1 <- data.frame(  
        Product = pro,
        Name = selected_dataname,
        TypeOfPurchase = selected_datapurchaseType,
        Date = selected_dataDate, 
        IndividualRating = selected_rate,
        ReviewText = selected_review
)
combinedProducts1 

#write csv for product 1 review
write.csv(combinedProducts1, file = "1stProduct.csv")

#load product 1 Samsung Galaxy Buds2 Pro, Graphite
head(combinedProducts1)
```
Second Product
```{r} 
#Get 13 Names
URL2 <- "https://www.amazon.com.au/product-reviews/B0CB8HHS8V/ref=acr_dpx_hist_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews#reviews-filter-bar"
session <- bow(URL2, user_agent = "Educational Purposes")
session

url2 <- read_html(URL2)  

#Get 12 Names
URL2.0 <- "https://www.amazon.com.au/product-reviews/B0CB8HHS8V/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=2#reviews-filter-bar"
session <- bow(URL2.0, user_agent = "Educational Purposes")
session

url2.0 <- read_html(URL2.0)

#Get 13 Names
URL2.1 <- "https://www.amazon.com.au/product-reviews/B0CB8HHS8V/ref=cm_cr_arp_d_paging_btm_next_4?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=4#reviews-filter-bar%22"
session <- bow(URL2.1, user_agent = "Educational Purposes")
session

url2.1 <- read_html(URL2.1)

#Get 12 Names
URL2.2 <- "https://www.amazon.com.au/product-reviews/B0CB8HHS8V/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=3#reviews-filter-bar"
session <- bow(URL2.2, user_agent = "Educational Purposes")
session

url2.2 <- read_html(URL2.2)
```
Second Product
```{r}
#Get 19 Reviewer Names
names2 <- url2%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names2

#Get 13 Names
names2.0 <- url2.0%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names2.0  <- names2.0[3:15] 
names2.0

#Get the Reviewers Names
names2.1 <- url2.1%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names2.1   

#Get 10 Reviewers Names
names2.2 <- url2.2%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names2.2 <- names2.2[3:12]
names2.2

#Type of Purhcase 
purchasetype2 <- url2%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()
purchasetype2 

purchasetype2.0 <- url2.0%>%
      html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
      html_text()
purchasetype2.0
  
purchasetype2.1 <- url2.1%>%
      html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
      html_text()
purchasetype2.1
  
purchasetype2.2 <- url2.2%>%
      html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
      html_text()
purchasetype2.2 <- purchase2.2[1:22] 
purchasetype2.2
  
#Date of Review
daterev2 <- url2%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()
daterev2

daterev2.0 <- url2.0%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()
daterev2.0

daterev2.1 <- url2.1%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()
daterev2.1 

daterev2.2 <- url2.2%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()
daterev2.2 

#Subset
daterevs2.2 <- daterev2.2[1:20] 

#Individual Ratings 
rates2 <- url2%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()
rates2

rates2.0 <- url2.0%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()
rates2.0

rates2.1 <- url2.1%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()
rates2.1 

rates2.2<- url2.2%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()
rates2.2

#Review Texts
reviews2 <- url2%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>% 
 gsub("\\n", "", .)
reviews2 

reviews2.0 <- url2.0%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>% 
 gsub("\\n", "", .)

reviews2.1 <- url2.1%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>%
 gsub("\\n", "", .)

reviews2.2 <- url2.2%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text()  %>%
 gsub("\\n", "", .)
reviews2.2 <- reviews2.2[1:30]

# DATA FRAMES
dataname2 <- data.frame(
    ReviewerName = c(names2, names2.0, names2.1, names2.2)[1:50]
)

datapurchaseType2 <- data.frame(
    TypeOfPurchase = c(purchasetype2, purchasetype2.0, purchasetype2.1, purchasetype2.2)[1:50]
)

dataDate2 <- data.frame(
    Date = c(daterev2, daterev2.0, daterev2.1, daterevs2.2)[1:50]
)

rate2 <- data.frame(
    IndividualRating = c(rates2, rates2.0, rates2.1, rates2.2)[1:50]
)

review_dataframe2 <- data.frame(
    ReviewText = c(reviews2, reviews2.0, reviews2.1, reviews2.2)[1:50]
)

 pro2 <- rep(subset24products[2],50) 
 
combinedProducts2 <- data.frame( 
   Product = pro2,
   ReviewerName = dataname2$ReviewerName,
   TypeOfPurchase = datapurchaseType2$TypeOfPurchase,
   Date = dataDate2$Date,
   IndividualRating = rate2$IndividualRating,
  ReviewText = review_dataframe2$ReviewText
)

combinedProducts2

#Product 2 csv
write.csv(combinedProducts2, file = "2ndProduct.csv")
#load 
head(combinedProducts2)
```
Third Product
```{r} 
URL3 <- "https://www.amazon.com.au/product-reviews/B07QKYTGH9/ref=acr_dpx_hist_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews#reviews-filter-bar"
session <- bow(URL3, user_agent = "Educational Purposes")
session

url3 <- read_html(URL3)  

#Get 12 
URL3.1 <- "https://www.amazon.com.au/product-reviews/B07QKYTGH9/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=2#reviews-filter-bar"
session <- bow(URL3.1, user_agent = "Educational Purposes")
session

url3.1 <- read_html(URL3.1)

URL3.2 <- "https://www.amazon.com.au/product-reviews/B07QKYTGH9/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=3#reviews-filter-bar"
session <- bow(URL3.2, user_agent = "Educational Purposes")
session

url3.2 <- read_html(URL3.2)

#Get 12
URL3.3 <- "https://www.amazon.com.au/product-reviews/B07QKYTGH9/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=4#reviews-filter-bar"
session <- bow(URL3.3, user_agent = "educational purposes")
session

url3.3 <- read_html(URL3.3)

URL3.4 <- "https://www.amazon.com.au/product-reviews/B07QKYTGH9/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=5#reviews-filter-bar"
session <- bow(URL3.4, user_agent = "Educational Purposes")
session

url3.4 <- read_html(URL3.4)
```
Third Product
```{r}
#Get 19 Reviewer Names
names3 <- url3%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names3

#Get 13
names3.1 <- url3.1%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names3.1  <- names3.1[3:13] 
names3.1

names3.2 <- url3.2%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names3.2 <- names3.2 [3:9] 
names3.2
#Get 10 
names3.3 <- url3.3%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names3.3 <- names3.3[3:12]
names3.3

names3.4 <- url3.4 %>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names3.4 <- names3.4[3:12]
names3.4

#Type of Purhcase 
purchasetype3<- url3%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()
purchasetype3

purchasetype3.1 <- url3.1%>%
      html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
      html_text()
purchasetype3.1
  
purchasetype3.2<- url3.2%>%
      html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
      html_text()
purchasetype3.2
  
purchasetype3.3 <- url3.3%>%
      html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
      html_text()
purchasetype3.3 <- purchasetype3.3 
purchasetype3.3 
  
purchasetype3.4 <- url3.4%>%
      html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
      html_text()
purchasetype3.4 <- purchasetype3.4 
purchasetype3.4

#Date of Review
daterev3<- url3%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()
daterev3

daterev3.1<- url3.1%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()
daterev3.1

daterev3.2<- url3.2%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()
daterev3.2 

daterev3.3<- url3.3%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()
daterev3.3 

#Subset
daterevs3.3 <- daterev3.3[1:20]

#Individual Ratings 
rates3<- url3%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()
rates3

rates3.1<- url3.1%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()
rates3.1

rates3.2<- url3.2%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()
rates3.2 

rates3.3<- url3.3%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()
rates3.3

#Reviews
reviews3 <- url3%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>% 
 gsub("\\n", "", .)
reviews3 

reviews3.1 <- url3.1%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>% 
 gsub("\\n", "", .)

reviews3.2 <- url3.2%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>%
 gsub("\\n", "", .)

reviews3.3 <- url3.3%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text()  %>%
 gsub("\\n", "", .)
reviews3.3<- reviews3.3[1:12]   

reviews3.4<- url3.4 %>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text()  %>%
 gsub("\\n", "", .)
reviews3.4<- reviews3.4[1:10]
 
# DATA FRAMES
dataname3 <- data.frame(
    ReviewerName = c(names3, names3.1, names3.2, names3.3,names3.4)[1:50]
)
dataname3

datapurchaseType3 <- data.frame(
    TypeOfPurchase = c(purchasetype3, purchasetype3.1, purchasetype3.2, purchasetype3.3, purchasetype3.4)[1:50]
)
datapurchaseType3

dataDate3 <- data.frame(
    Date = c(daterev3, daterev3.1, daterev3.2, daterevs3.3)[1:50]
)

rate3 <- data.frame(
    IndividualRating = c(rates3, rates3.1, rates3.2, rates3.3)[1:50]
)

review_dataframe3 <- data.frame(
    ReviewText = c(reviews3, reviews3.1, reviews3.2, reviews3.3,reviews3.4)[1:50]
)

     pro3 <- rep(subset24products[3],50) 
     
combinedProducts3 <- data.frame( 
          Product = pro3,
          ReviewerName = dataname3$ReviewerName,
          TypeOfPurchase = datapurchaseType3$TypeOfPurchase,
          Date = dataDate3$Date,
          IndividualRating = rate3$IndividualRating,
          ReviewText = review_dataframe3$ReviewText
)

combinedProducts3
#Product 3 csv
write.csv(combinedProducts3, file = "3rdProduct.csv")
head(combinedProducts3)
```
Fourth Product
```{r}
URL4 <- "https://www.amazon.com.au/product-reviews/B085RN9GRX/ref=acr_search_hist_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews#reviews-filter-bar"
session <- bow(URL4, user_agent = "Educational Purposes")
session

url4 <- read_html(URL4)  

#Get 12
URL4.1 <- "https://www.amazon.com.au/product-reviews/B07QKYTGH9/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=2#reviews-filter-bar"
session <- bow(URL4.1, user_agent = "Educational Purposes")
session

url4.1 <- read_html(URL4.1)

URL4.2 <- "https://www.amazon.com.au/product-reviews/B085RN9GRX/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=3#reviews-filter-bar"
session <- bow(URL4.2, user_agent = "Educational Purposes")
session

url4.2 <- read_html(URL4.2)

URL4.3 <- "https://www.amazon.com.au/product-reviews/B085RN9GRX/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=4#reviews-filter-bar"
session <- bow(URL4.3, user_agent = "Educational Purposes")
session

url4.3 <- read_html(URL4.3)

URL4.4 <- "https://www.amazon.com.au/product-reviews/B085RN9GRX/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=5#reviews-filter-bar"
session <- bow(URL4.4, user_agent = "Educational Purposes")
session

url4.4 <- read_html(URL4.4)
```
Fourth Product
```{r}
#Reviwer's Namess
names4 <- url4%>%
    html_nodes("div.a-profile-content") %>%
    html_text()

names4.1 <- url4.1%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names4.1 <- names4.1[3:13] 

names4.2 <- url4.2%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names4.2 <- names4.2[3:9] 

names4.3 <- url4.3%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names4.3 <- names4.3[3:12]

names4.4 <- url4.4%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names4.4 <- names4.4[3:12]

#Type of Purchase
purchasetype4 <- url4%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype4.1 <- url4.1%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype4.2 <- url4.2%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype4.3 <- url4.3%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype4.4 <- url4.4%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

#Date of Review
daterev4 <- url4%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()
 
daterev4.1 <- url4.1%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev4.2 <- url4.2%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev4.3 <- url4.3 %>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev4.4 <- url4.4 %>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()
#Subset
daterevs4.3 <- daterev4.3[1:20] 

#Individual Ratings 
rates4 <- url4%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates4.1 <- url4.1%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates4.2 <- url4.2%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates4.3 <- url4.3%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates4.4 <- url4.4%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

#Reviews
reviews4 <- url4%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>% 
    gsub("\\n", "", .)

reviews4.1 <- url4.1%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>% 
    gsub("\\n", "", .)

reviews4.2 <- url4.2%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>%
    gsub("\\n", "", .)

reviews4.3 <- url4.3%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text()  %>%
    gsub("\\n", "", .)
reviews4.3 <- reviews4.3[1:12]   

reviews4.4 <- url4.4%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text()  %>%
    gsub("\\n", "", .)
reviews4.4 <- reviews4.4[1:10]

#Data Frames
dataname4 <- data.frame(
    ReviewerName = c(names4, names4.1, names4.2, names4.3, names4.4)[1:50]
)
dataname4

datapurchaseType4 <- data.frame(
    TypeOfPurchase = c(purchasetype4, purchasetype4.1, purchasetype4.2, purchasetype4.3, purchasetype4.4)[1:50]
)
datapurchaseType4

dataDate4 <- data.frame(
    Date = c(daterev4, daterev4.1, daterev4.2, daterevs4.3)[1:50]
)

rate4 <- data.frame(
    IndividualRating = c(rates4, rates4.1, rates4.2, rates4.3)[1:50]
)


review_dataframe4 <- data.frame(
    ReviewText = c(reviews4, reviews4.1, reviews4.2, reviews4.3, reviews4.4)[1:50]
)
    
     pro4 <- rep(subset24products[4],50)
     
combinedProducts4 <- data.frame( 
  Product = pro4,
  ReviewerName = dataname4$ReviewerName,
  TypeOfPurchase = datapurchaseType4$TypeOfPurchase,
  Date = dataDate4$Date,
  IndividualRating = rate4$IndividualRating,
  ReviewText = review_dataframe4$ReviewText
)

combinedProducts4
#Product 4 csv
write.csv(combinedProducts4, file = "4thProduct.csv")

```
Fifth Product
```{r}
URL5<- "https://www.amazon.com.au/product-reviews/B0BHDRW3MK/ref=acr_dpx_hist_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews#reviews-filter-bar"
session <- bow(URL5, user_agent = "Educational Purposes")
session

url5 <- read_html(URL5)

URL5.1 <- "https://www.amazon.com.au/product-reviews/B0BHDRW3MK/ref=acr_dpx_hist_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews#reviews-filter-bar"
session <- bow(URL5.1, user_agent = "Educational Purposes")
session

url5.1 <- read_html(URL5.1)

URL5.2 <- "https://www.amazon.com.au/product-reviews/B0BHDRW3MK/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=2#reviews-filter-bar"
session <- bow(URL5.2, user_agent = "educational purposes")
session

url5.2 <- read_html(URL5.2)

# This link adds 12
URL5.3 <- "https://www.amazon.com.au/product-reviews/B0BHDRW3MK/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=3#reviews-filter-bar"
session <- bow(URL5.3, user_agent = "educational purposes")
session

url5.3 <- read_html(URL5.3)

URL5.4 <- "https://www.amazon.com.au/product-reviews/B0BHDRW3MK/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=4#reviews-filter-bar"
session <- bow(URL5.4, user_agent = "educational purposes")
session

url5.4 <- read_html(URL5.4)
```
Fifth Product 
```{r}
#Reviwers Names
names5 <- url5%>%
    html_nodes("div.a-profile-content") %>%
    html_text()

names5.1 <- url5.1%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names5.1 <- names5.1[3:13] 

names5.2 <- url5.2%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names5.2 <- names5.2[3:9] 

names5.3 <- url5.3%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names5.3 <- names5.3[3:12]

names5.4 <- url5.4%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names5.4 <- names5.4[3:12]

#Type of purchase 
purchasetype5 <- url5%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype5.1 <- url5.1%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype5.2 <- url5.2%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype5.3 <- url5.3%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype5.4 <- url5.4%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

#Date of Review 
daterev5 <- url5%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev5.1 <- url5.1%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev5.2 <- url5.2%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev5.3 <- url5.3%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev5.4 <- url5.4%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

#Subset
daterevs5.3 <- daterev5.4[1:20]

#Individual Ratings
rates5 <- url5%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates5.1 <- url5.1%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates5.2 <- url5.2 %>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates5.3 <- url5.3%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates5.4 <- url5.4%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

#Reviews 
reviews5 <- url5%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>% 
    gsub("\\n", "", .)

reviews5.1 <- url5.1%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>% 
    gsub("\\n", "", .)

reviews5.2 <- url5.2%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>%
    gsub("\\n", "", .)

reviews5.3 <- url5.3%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text()  %>%
    gsub("\\n", "", .)
reviews5.3 <- reviews5.3[1:12]   

reviews5.4 <- url5.4%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text()  %>%
    gsub("\\n", "", .)
reviews5.4 <- reviews5.4[1:10]

#Data Frames
dataname5 <- data.frame(
    ReviewerName = c(names5, names5.1, names5.2, names5.3, names5.4)[1:50]
)
dataname5

datapurchaseType5 <- data.frame(
    TypeOfPurchase = c(purchasetype5, purchasetype5.1, purchasetype5.2, purchasetype5.3, purchasetype5.4)[1:50]
)
datapurchaseType5

dataDate5 <- data.frame(
    Date = c(daterev5, daterev5.1, daterev5.2, daterevs5.3)[1:50]
)

rate5 <- data.frame(
    IndividualRating = c(rates5, rates5.1, rates5.2, rates5.3)[1:50]
)

review_dataframe5 <- data.frame(
    ReviewText = c(reviews5, reviews5.1, reviews5.2, reviews5.3, reviews5.4)[1:50]
) 

 pro5 <- rep(subset24products[5],50)
 
combinedProducts5 <- data.frame( 
  Product = pro5,
  ReviewerName = dataname5$ReviewerName,
  TypeOfPurchase = datapurchaseType5$TypeOfPurchase,
  Date = dataDate5$Date,
  IndividualRating = rate5$IndividualRating,
  ReviewText = review_dataframe5$ReviewText
)

combinedProducts5

#Product 5 csv
write.csv(combinedProducts5, file = "5thProduct.csv")
```
Sixth Product
```{r} 
URL6<- "https://www.amazon.com.au/product-reviews/B0CCVCPCNR/ref=acr_search_hist_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews#reviews-filter-bar"
session <- bow(URL6, user_agent = "Educational Purposes")
session

url6 <- read_html(URL6)

URL6.1 <- "https://www.amazon.com.au/product-reviews/B0CCVCPCNR/ref=acr_search_hist_4?ie=UTF8&filterByStar=four_star&reviewerType=all_reviews#reviews-filter-bar" 
session <- bow(URL6.1, user_agent = "Educational Purposes")
session

url6.1 <- read_html(URL6.1)

URL6.2 <- "https://www.amazon.com.au/product-reviews/B0CCVCPCNR/ref=acr_search_hist_3?ie=UTF8&filterByStar=three_star&reviewerType=all_reviews#reviews-filter-bar" 
session <- bow(URL6.2, user_agent = "Educational Purposes")
session

url6.2 <- read_html(URL6.2)

URL6.3 <- "https://www.amazon.com.au/product-reviews/B0CCVCPCNR/ref=acr_search_hist_2?ie=UTF8&filterByStar=two_star&reviewerType=all_reviews#reviews-filter-bar"
session <- bow(URL6.3, user_agent = "Educational Purposes")
session

url6.3 <- read_html(URL6.3)

URL6.4 <- "https://www.amazon.com.au/product-reviews/B0BHDRW3MK/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=4#reviews-filter-bar"
session <- bow(URL6.4, user_agent = "Educational Purposes")
session

url6.4 <- read_html(URL6.4)
```
```{r}
#Reviewers Names
names6 <- url6%>%
    html_nodes("div.a-profile-content") %>%
    html_text() 
names6

names6.1 <- url6.1%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names6.1 <- names6.1[3:11] 
names6.1

#Get 12 
names6.2 <- url6.2%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names6.2 <- names6.2[3:9] 
names6.2

#Get 10
names6.3 <- url6.3%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names6.3 <- names6.3[3:12]
names6.3 

#Type of Purchase 
purchasetype6 <- url6%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype6.1 <- url6.1%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype6.2 <- url6.2%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype6.3 <- url6.3%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype6.4 <- url6.4%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

#Date of Review
daterev6 <- url6%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev6.1 <- url6.1%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev6.2 <- url6.2%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev6.3 <- url6.3%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev6.4 <- url6.4%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

#Subset
daterevs6.3 <- daterev6.4[1:20]

#Individual Ratings 
rates6 <- url6%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates6.1 <- url6.1%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates6.2 <- url6.2%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates6.3 <- url6.3%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates6.4 <- url6.4%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

#Reviews
reviews6 <- url6%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>% 
    gsub("\\n", "", .)

reviews6.1 <- url6.1%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>% 
    gsub("\\n", "", .)

reviews6.2 <- url6.2%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>%
    gsub("\\n", "", .)

reviews6.3 <- url6.3%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text()  %>%
    gsub("\\n", "", .)
reviews6.3 <- reviews6.3[1:12]   

reviews6.4 <- url6.4%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text()  %>%
    gsub("\\n", "", .)
reviews6.4 <- reviews6.4[1:10]

#Data Frames
dataname6 <- data.frame(
    ReviewerName = c(names6, names6.1, names6.2, names6.3)[1:50]
)

datapurchaseType6 <- data.frame(
    TypeOfPurchase = c(purchasetype6, purchasetype6.1, purchasetype6.2, purchasetype6.3, purchasetype6.4)[1:50]
)

dataDate6 <- data.frame(
    Date = c(daterev6, daterev6.1, daterev6.2, daterev6.3)[1:50]
)

rate6 <- data.frame(
    IndividualRating = c(rates6, rates6.1, rates6.2, rates6.3)[1:50]
)

review_dataframe6 <- data.frame(
    ReviewText = c(reviews6, reviews6.1, reviews6.2, reviews6.3, reviews6.4)[1:50]
) 

 pro6 <- rep(subset24products[6],50) 
  
combinedProducts6 <- data.frame( 
        Product =  pro6,
        ReviewerName = dataname6$ReviewerName,
        TypeOfPurchase = datapurchaseType6$TypeOfPurchase,
        Date = dataDate6$Date,
        IndividualRating = rate6$IndividualRating,
        ReviewText = review_dataframe6$ReviewText
)
combinedProducts6

#Product 6 csv
write.csv(combinedProducts6, file = "6thProducts.csv")
```
Seventh Product
```{r}
URL7 <- "https://www.amazon.com.au/product-reviews/B0C8HCSL1Z/ref=acr_search_hist_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews#reviews-filter-bar" 
session <- bow(URL7, user_agent = "Educational Purposes")
session

url7 <- read_html(URL7)

URL7.1 <- "https://www.amazon.com.au/product-reviews/B0C8HCSL1Z/ref=acr_search_hist_4?ie=UTF8&filterByStar=four_star&reviewerType=all_reviews#reviews-filter-bar" 
session <- bow(URL7.1, user_agent = "Educational Purposes")
session

url7.1 <- read_html(URL7.1)

URL7.2 <- "https://www.amazon.com.au/product-reviews/B0C8HCSL1Z/ref=acr_search_hist_3?ie=UTF8&filterByStar=three_star&reviewerType=all_reviews#reviews-filter-bar" 
session <- bow(URL7.2, user_agent = "Educational Purposes")
session

url7.2 <- read_html(URL7.2)

URL7.3 <- "https://www.amazon.com.au/product-reviews/B0C8HCSL1Z/ref=acr_search_hist_2?ie=UTF8&filterByStar=two_star&reviewerType=all_reviews#reviews-filter-bar"
session <- bow(URL7.3, user_agent = "Educational Purposes")
session

url7.3 <- read_html(URL7.3)

URL7.4 <- "https://www.amazon.com.au/product-reviews/B0C8HCSL1Z/ref=acr_search_hist_1?ie=UTF8&filterByStar=one_star&reviewerType=all_reviews#reviews-filter-bar"
session <- bow(URL7.4, user_agent = "Educational Purposes")
session

url7.4 <- read_html(URL7.4)
```
Seventh Product
```{r}
#Reviewers Names
names7 <- url7%>%
    html_nodes("div.a-profile-content") %>%
    html_text() 
names7

names7.1 <- url7.1%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names7.1 <- names7.1[3:11] 
names7.1

names7.2 <- url7.2%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names7.2 <- names7.2[3:9] 
names7.2

names7.3 <- url7.3%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names7.3 <- names7.3[3:12]
names7.3 

#Type of Purchase 
purchasetype7 <- url7%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype7.1 <- url7.1%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype7.2 <- url7.2%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype7.3 <- url7.3%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype7.4 <- url7.4%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

#Date of Review 
daterev7 <- url7%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev7.1 <- url7.1%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev7.2 <- url7.2%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev7.3 <- url7.3%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev7.4 <- url7.4%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

#Subset
daterevs7.3 <- daterev7.4[1:20]

#Individual ratings 
rates7 <- url7%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates7.1 <- url7.1%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates7.2 <- url7.2%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates7.3 <- url7.3%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates7.4 <- url7.4%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

#Reviews
reviews7 <- url7%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>% 
    gsub("\\n", "", .)

reviews7.1 <- url7.1%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>% 
    gsub("\\n", "", .)

reviews7.2 <- url7.2%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>%
    gsub("\\n", "", .)

reviews7.3 <- url7.3%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text()  %>%
    gsub("\\n", "", .)
reviews7.3 <- reviews7.3[1:12]   

reviews7.4 <- url7.4%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text()  %>%
    gsub("\\n", "", .)
reviews7.4 <- reviews7.4[1:10] 

#Data Frames
dataname7 <- data.frame(
    ReviewerName = c(names7, names7.1, names7.2, names7.3 )[1:50]
)
dataname7

datapurchaseType7 <- data.frame(
    TypeOfPurchase = c(purchasetype7, purchasetype7.1, purchasetype7.2, purchasetype7.3, purchasetype7.4)[1:50]
)
datapurchaseType7

dataDate7 <- data.frame(
    Date = c(daterev7, daterev7.1, daterev7.2, daterevs7.3)[1:50]
)

rate7 <- data.frame(
    IndividualRating = c(rates7, rates7.1, rates7.2, rates7.3)[1:50]
)

review_dataframe7 <- data.frame(
    ReviewText = c(reviews7, reviews7.1, reviews7.2, reviews7.3, reviews7.4)[1:50]
)
 pro7 <- rep(subset24products[7],50)

combinedProducts7 <- data.frame( 
          Product = pro7,
          ReviewerName = dataname7$ReviewerName,
          TypeOfPurchase = datapurchaseType7$TypeOfPurchase,
          Date = dataDate7$Date,
          IndividualRating = rate7$IndividualRating,
          ReviewText = review_dataframe7$ReviewText
)
combinedProducts7

#Product 7 csv 
write.csv(combinedProducts7, file = "7thProducts.csv")
```
Eighth Product 
```{r}
URL8 <- "https://www.amazon.com.au/product-reviews/B09WMJCQRM/ref=acr_search_hist_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews#reviews-filter-bar" 
session <- bow(URL8, user_agent = "Educational Purposes")
session

url8 <- read_html(URL8)

URL8.1 <- "https://www.amazon.com.au/product-reviews/B09WMJCQRM/ref=acr_search_hist_4?ie=UTF8&filterByStar=four_star&reviewerType=all_reviews#reviews-filter-bar" 
session <- bow(URL8.1, user_agent = "Educational Purposes")
session

url8.1 <- read_html(URL8.1)

URL8.2 <- "https://www.amazon.com.au/product-reviews/B09WMJCQRM/ref=acr_search_hist_three?ie=UTF8&filterByStar=three_star&reviewerType=all_reviews#reviews-filter-bar" 
session <- bow(URL8.2, user_agent = "Educational Purposes")
session

url8.2 <- read_html(URL8.2)

URL8.3 <- "https://www.amazon.com.au/product-reviews/B09WMJCQRM/ref=acr_search_hist_2?ie=UTF8&filterByStar=two_star&reviewerType=all_reviews#reviews-filter-bar"
session <- bow(URL8.3, user_agent = "Educational Purposes")
session

url8.3 <- read_html(URL8.3)

URL8.4 <- "https://www.amazon.com.au/product-reviews/B09WMJCQRM/ref=acr_search_hist_1?ie=UTF8&filterByStar=one_star&reviewerType=all_reviews#reviews-filter-bar"
session <- bow(URL8.4, user_agent = "Educational Purposes")
session

url8.4 <- read_html(URL8.4)
```
Eighth Product
```{r}
#Reviewers Names
names8 <- url8%>%
    html_nodes("div.a-profile-content") %>%
    html_text() 
names8

#Get 12
names8.1 <- url8.1%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names8.1 <- names8.1[3:11] 
names8.1

names8.2 <- url8.2%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names8.2 <- names8.2[3:9] 
names8.2

names8.3 <- url8.3%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names8.3 <- names8.3[3:12]
names8.3 

#Type of Purchase 
purchasetype8 <- url8%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype8.1 <- url8.1%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype8.2 <- url8.2%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype8.3 <- url8.3%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype8.4 <- url8.4%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

#Date of Review
daterev8 <- url8%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev8.1 <- url8.1%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev8.2 <- url8.2%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev8.3 <- url8.3%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev8.4 <- url8.4%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

#Subset
daterevs8.3 <- daterev8.4[1:20]

#Individual ratings 
rates8 <- url8%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates8.1 <- url8.1%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates8.2 <- url8.2%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates8.3 <- url8.3%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates8.4 <- url8.4%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

#Reviews
reviews8 <- url8%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>% 
    gsub("\\n", "", .)

reviews8.1 <- url8.1%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>% 
    gsub("\\n", "", .)

reviews8.2 <- url8.2%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>%
    gsub("\\n", "", .)

reviews8.3 <- url8.3%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text()  %>%
    gsub("\\n", "", .)
reviews8.3 <- reviews8.3[1:12]   

reviews8.4 <- url8.4%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text()  %>%
    gsub("\\n", "", .)
reviews8.4 <- reviews8.4[1:10]

#Data Frames
dataname8 <- data.frame(
    ReviewerName = c(names8, names8.1, names8.2, names8.3)[1:50]
)

datapurchaseType8 <- data.frame(
    TypeOfPurchase = c(purchasetype8, purchasetype8.1, purchasetype8.2, purchasetype8.3, purchasetype8.4)[1:50]
)

dataDate8 <- data.frame(
    Date = c(daterev8, daterev8.1, daterev8.2, daterev8.3)[1:50]
)

rate8 <- data.frame(
    IndividualRating = c(rates8, rates8.1, rates8.2, rates8.3)[1:50]
)

review_dataframe8 <- data.frame(
    ReviewText = c(reviews8, reviews8.1, reviews8.2, reviews8.3, reviews8.4)[1:50]
) 

 pro8 <- rep(subset24products[8],50) 
 
combinedProducts8 <- data.frame( 
        Product = pro8,
        ReviewerName = dataname8$ReviewerName,
        TypeOfPurchase = datapurchaseType8$TypeOfPurchase,
        Date = dataDate8$Date,
        IndividualRating = rate8$IndividualRating,
        ReviewText = review_dataframe8$ReviewText
)

combinedProducts8

#Product 8 Reviews
write.csv(combinedProducts8, file = "8thProducts.csv")
```
Nineth Product
```{r}
URL9 <- "https://www.amazon.com.au/product-reviews/B0CMZTG3YN/ref=acr_search_hist_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews#reviews-filter-bar"
session <- bow(URL9, user_agent = "Educational Purposes")
session

url9 <- read_html(URL9)

URL9.1 <- "https://www.amazon.com.au/product-reviews/B0CMZTG3YN/ref=acr_search_hist_4?ie=UTF8&filterByStar=four_star&reviewerType=all_reviews#reviews-filter-bar" 
session <- bow(URL9.1, user_agent = "Educational Purposes")
session

url9.1 <- read_html(URL9.1)

URL9.2 <- "https://www.amazon.com.au/product-reviews/B0CMZTG3YN/ref=acr_search_hist_3?ie=UTF8&filterByStar=three_star&reviewerType=all_reviews#reviews-filter-bar" 
session <- bow(URL9.2, user_agent = "Educational Purposes")
session

url9.2 <- read_html(URL9.2)

URL9.3 <- "https://www.amazon.com.au/product-reviews/B0CMZTG3YN/ref=acr_search_hist_2?ie=UTF8&filterByStar=two_star&reviewerType=all_reviews#reviews-filter-bar"
session <- bow(URL9.3, user_agent = "Educational Purposes")
session

url9.3 <- read_html(URL9.3)

URL9.4 <- "https://www.amazon.com.au/product-reviews/B0CMZTG3YN/ref=acr_search_hist_1?ie=UTF8&filterByStar=one_star&reviewerType=all_reviews#reviews-filter-bar"
session <- bow(URL9.4, user_agent = "Educational Purposes")
session

url9.4 <- read_html(URL9.4)
```
Nineth Product
```{r}
#Reviewers Names
names9 <- url9%>%
    html_nodes("div.a-profile-content") %>%
    html_text() 
names9

names9.1 <- url9.1%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names9.1 <- names9.1[3:11] 
names9.1

names9.2 <- url9.2%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names9.2 <- names9.2[3:9] 
names9.2

names9.3 <- url9.3%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names9.3 <- names9.3[3:12]
names9.3 

#Type of purchase 
purchasetype9 <- url9%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype9.1 <- url9.1%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype9.2 <- url9.2%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype9.3 <- url9.3%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype9.4 <- url9.4%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

#Date of Review  
daterev9 <- url9%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev9.1 <- url9.1%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev9.2 <- url9.2%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev9.3 <- url9.3%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev9.4 <- url9.4%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

#Subset
daterevs9.3 <- daterev9.4[1:20]

#Individual ratings 
rates9 <- url9%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

# Individual ratings 
rates9.1 <- url9.1%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates9.2 <- url9.2%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates9.3 <- url9.3%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates9.4 <- url9.4%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

#Reviews
reviews9 <- url9%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>% 
    gsub("\\n", "", .)

reviews9.1 <- url9.1%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>% 
    gsub("\\n", "", .)

reviews9.2 <- url9.2%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>%
    gsub("\\n", "", .)

reviews9.3 <- url9.3%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text()  %>%
    gsub("\\n", "", .)
reviews9.3 <- reviews9.3[1:12]   

reviews9.4 <- url9.4%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text()  %>%
    gsub("\\n", "", .)
reviews9.4 <- reviews9.4[1:10]

#Data Frames
dataname9 <- data.frame(
    ReviewerName = c(names9, names9.1, names9.2, names9.3)[1:50]
)

datapurchaseType9 <- data.frame(
    TypeOfPurchase = c(purchasetype9, purchasetype9.1, purchasetype9.2, purchasetype9.3, purchasetype9.4)[1:50]
)

dataDate9 <- data.frame(
    Date = c(daterev9, daterev9.1, daterev9.2, daterev9.3)[1:50]
)

rate9 <- data.frame(
    IndividualRating = c(rates9, rates9.1, rates9.2, rates9.3)[1:50]
)

review_dataframe9 <- data.frame(
    ReviewText = c(reviews9, reviews9.1, reviews9.2, reviews9.3, reviews9.4)[1:50]
) 

 pro9 <- rep(subset24products[9],50) 
 
combinedProducts9 <- data.frame( 
          Product = pro9,
          ReviewerName = dataname9$ReviewerName,
          TypeOfPurchase = datapurchaseType9$TypeOfPurchase,
          Date = dataDate9$Date,
          IndividualRating = rate9$IndividualRating,
          ReviewText = review_dataframe9$ReviewText
)

combinedProducts9

#Product 9 Reviews
write.csv(combinedProducts9, file = "9thProducts.csv")
```
Tenth Product
```{r}
URL10 <- "https://www.amazon.com.au/product-reviews/B0CFXWNPP2/ref=acr_search_hist_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews#reviews-filter-bar"
session <- bow(URL10, user_agent = "Educational Purposes")
session

url10 <- read_html(URL10)

URL10.1 <- "https://www.amazon.com.au/product-reviews/B0CFXWNPP2/ref=acr_search_hist_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews#reviews-filter-bar"
session <- bow(URL10.1, user_agent = "Educational Purposes")
session

url10.1 <- read_html(URL10.1)

URL10.2 <- "https://www.amazon.com.au/product-reviews/B0CFXWNPP2/ref=acr_search_hist_4?ie=UTF8&filterByStar=four_star&reviewerType=all_reviews#reviews-filter-bar"
session <- bow(URL10.2, user_agent = "Educational Purposes")
session

url10.2 <- read_html(URL10.2)

URL10.3 <- "https://www.amazon.com.au/product-reviews/B0CFXWNPP2/ref=acr_search_hist_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews#reviews-filter-bar"
session <- bow(URL10.3, user_agent = "Educational Purposes")
session

url10.3 <- read_html(URL10.3)

URL10.4 <- "https://www.amazon.com.au/product-reviews/B0CFXWNPP2/ref=acr_search_hist_3?ie=UTF8&filterByStar=three_star&reviewerType=all_reviews#reviews-filter-bar"
url10.4 <- read_html(URL10.4)
```
Tenth Product
```{r}
#Reviewers Names
names10 <- url10%>%
    html_nodes("div.a-profile-content") %>%
    html_text() 
names10

names10.1 <- url10.1 %>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names10.1 <- names10.1[3:11] 
names10.1

names10.2 <- url10.2 %>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names10.2 <- names10.2[3:9] 
names10.2

names10.3 <- url10.3 %>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names10.3 <- names10.3[3:12]
names10.3

#Type of purchase 
purchasetype10 <- url10%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype10.1 <- url10.1%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype10.2 <- url10.2 %>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype10.3 <- url10.3 %>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype10.4 <- url10.4 %>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

#Date of Review 
daterev10 <- url10%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev10.1 <- url10.1%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev10.2 <- url10.2%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev10.3 <- url10.3 %>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev10.4 <- url10.4 %>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

#Subset
daterevs10.3 <- daterev10.4[1:20]

#Individual Ratings 
rates10 <- url10%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates10.1 <- url10.1%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates10.2 <- url10.2%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()
 
rates10.3 <- url10.3%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates10.4 <- url10.4%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

#Reviews
reviews10 <- url10%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>% 
    gsub("\\n", "", .)

reviews10.1 <- url10.1%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>% 
    gsub("\\n", "", .)

reviews10.2 <- url10.2%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>%
    gsub("\\n", "", .)

reviews10.3 <- url10.3%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text()  %>%
    gsub("\\n", "", .)
reviews10.3 <- reviews10.3[1:12]   

reviews10.4 <- url10.4%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text()  %>%
    gsub("\\n", "", .)
reviews10.4 <- reviews10.4[1:10]

# DATA FRAMES
dataname10 <- data.frame(
    ReviewerName = c(names10, names10.1, names10.2, names10.3)[1:50]
)

datapurchaseType10 <- data.frame(
    TypeOfPurchase = c(purchasetype10, purchasetype10.1, purchasetype10.2, purchasetype10.3, purchasetype10.4)[1:50]
)

dataDate10 <- data.frame(
    Date = c(daterev10, daterev10.1, daterev10.2, daterev10.3)[1:50]
)

rate10 <- data.frame(
    IndividualRating = c(rates10, rates10.1, rates10.2, rates10.3)[1:50]
)

review_dataframe10 <- data.frame(
    ReviewText = c(reviews10, reviews10.1, reviews10.2, reviews10.3, reviews10.4)[1:50]
) 

 pro10 <- rep(subset24products[10],50)
 
combinedProducts10 <- data.frame( 
        Product = pro10,
        ReviewerName = dataname10$ReviewerName,
        TypeOfPurchase = datapurchaseType10$TypeOfPurchase,
        Date = dataDate10$Date,
        IndividualRating = rate10$IndividualRating,
        ReviewText = review_dataframe10$ReviewText
)

combinedProducts10

#Product 10 Reviews
write.csv(combinedProducts10, file = "10thProducts.csv")
```
Eleventh Product
```{r}
URL11 <- "https://www.amazon.com.au/product-reviews/B0CCVCPCNR/ref=acr_search_hist_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews#reviews-filter-bar"
session <- bow(URL11, user_agent = "Educational Purposes")
session

url11 <- read_html(URL11)

URL11.1 <- "https://www.amazon.com.au/product-reviews/B0CCVCPCNR/ref=acr_search_hist_4?ie=UTF8&filterByStar=four_star&reviewerType=all_reviews#reviews-filter-bar"
session <- bow(URL11.1, user_agent = "Educational Purposes")
session

url11.1 <- read_html(URL11.1)

URL11.2 <- "https://www.amazon.com.au/product-reviews/B0CCVCPCNR/ref=acr_search_hist_3?ie=UTF8&filterByStar=three_star&reviewerType=all_reviews#reviews-filter-bar"
session <- bow(URL11.2, user_agent = "Educational Purposes")
session

url11.2 <- read_html(URL11.2)

URL11.3 <- "https://www.amazon.com.au/product-reviews/B0CCVCPCNR/ref=acr_search_hist_2?ie=UTF8&filterByStar=two_star&reviewerType=all_reviews#reviews-filter-bar"
session <- bow(URL11.3, user_agent = "Educational Purposes")
session

url11.3 <- read_html(URL11.3)

URL11.4 <- "https://www.amazon.com.au/product-reviews/B0CCVCPCNR/ref=acr_search_hist_1?ie=UTF8&filterByStar=one_star&reviewerType=all_reviews#reviews-filter-bar"
url11.4 <- read_html(URL11.4)
```
Eleventh Product
```{r}
#Reviewers Names 
names11 <- url11%>%
    html_nodes("div.a-profile-content") %>%
    html_text() 
names11

names11.1 <- url11.1%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names11.1 <- names11.1[3:11] 
names11.1

names11.2 <- url11.2%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names11.2 <- names11.2[3:9] 
names11.2

names11.3 <- url11.3%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names11.3 <- names11.3[3:12]
names11.3

#Type of Purchase 
purchasetype11 <- url11%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype11.1 <- url11.1%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype11.2 <- url11.2%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype11.3 <- url11.3%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype11.4 <- url11.4%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

#Date of Review  
daterev11 <- url11%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev11.1 <- url11.1%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev11.2 <- url11.2%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev11.3 <- url11.3%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev11.4 <- url11.4%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

#Subset
daterevs11.3 <- daterev11.4[1:20]

#Individual ratings 
rates11 <- url11%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates11.1 <- url11.1%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates11.2 <- url11.2%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates11.3 <- url11.3%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates11.4 <- url11.4%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

#Reviews
reviews11 <- url11%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>% 
    gsub("\\n", "", .)

reviews11.1 <- url11.1%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>% 
    gsub("\\n", "", .)

reviews11.2 <- url11.2%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>%
    gsub("\\n", "", .)

reviews11.3 <- url11.3%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text()  %>%
    gsub("\\n", "", .)
reviews11.3 <- reviews11.3[1:12]   

reviews11.4 <- url11.4%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text()  %>%
    gsub("\\n", "", .)
reviews11.4 <- reviews11.4[1:10] 

#Data Frames
dataname11 <- data.frame(
    ReviewerName = c(names11, names11.1, names11.2, names11.3)[1:50]
)

datapurchaseType11 <- data.frame(
    TypeOfPurchase = c(purchasetype11, purchasetype11.1, purchasetype11.2, purchasetype11.3, purchasetype11.4)[1:50]
)

dataDate11 <- data.frame(
    Date = c(daterev11, daterev11.1, daterev11.2, daterev11.3)[1:50]
)

rate11 <- data.frame(
    IndividualRating = c(rates11, rates11.1, rates11.2, rates11.3)[1:50]
)

review_dataframe11 <- data.frame(
    ReviewText = c(reviews11, reviews11.1, reviews11.2, reviews11.3, reviews11.4)[1:50]
) 

pro11 <- rep(subset24products[11], 50)

combinedProducts11 <- data.frame( 
    Product = pro11,
    ReviewerName = dataname11$ReviewerName,
    TypeOfPurchase = datapurchaseType11$TypeOfPurchase,
    Date = dataDate11$Date,
    IndividualRating = rate11$IndividualRating,
    ReviewText = review_dataframe11$ReviewText
)

combinedProducts11

#Product 11 Reviews
write.csv(combinedProducts11, file = "11thProducts.csv")
```
Twelfth Product 
```{r}
URL12 <- "https://www.amazon.com.au/product-reviews/B0CMZVZPCF/ref=acr_search_hist_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews#reviews-filter-bar"
session <- bow(URL12, user_agent = "Educational Purposes")
session

url12 <- read_html(URL12)

URL12.1 <- "https://www.amazon.com.au/product-reviews/B0CMZVZPCF/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=2#reviews-filter-bar"
session <- bow(URL12.1, user_agent = "Educational Purposes")
session

url12.1 <- read_html(URL12.1)

URL12.2 <- "https://www.amazon.com.au/product-reviews/B0CMZVZPCF/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=3#reviews-filter-bar"
session <- bow(URL12.2, user_agent = "Educational Purposes")
session

url12.2 <- read_html(URL12.2)

URL12.3 <- "https://www.amazon.com.au/product-reviews/B0CMZVZPCF/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=4#reviews-filter-bar"
session <- bow(URL12.3, user_agent = "Educational Purposes")
session

url12.3 <- read_html(URL12.3)

URL12.4 <- "https://www.amazon.com.au/product-reviews/B0CMZVZPCF/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=5#reviews-filter-bar" 

url12.4 <- read_html(URL12.4)
```
Product 11
```{r}
#Reviewers Names
names12 <- url12%>%
    html_nodes("div.a-profile-content") %>%
    html_text() 
names12

names12.1 <- url12.1%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names12.1 <- names12.1[3:11] 
names12.1

names12.2 <- url12.2%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names12.2 <- names12.2[3:9] 
names12.2

names12.3 <- url12.3%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names12.3 <- names12.3[3:12]
names12.3

#Type of Purchase 
purchasetype12 <- url12%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype12.1 <- url12.1%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype12.2 <- url12.2%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype12.3 <- url12.3%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype12.4 <- url12.4%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

#Date of Review
daterev12 <- url12%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev12.1 <- url12.1%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev12.2 <- url12.2%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev12.3 <- url12.3%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev12.4 <- url12.4%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

#Subset 
daterevs12.3 <- daterev12.4[1:20]

#Individual Ratings 
rates12 <- url12%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates12.1 <- url12.1%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates12.2 <- url12.2%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates12.3 <- url12.3%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates12.4 <- url12.4%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

#Reviews
reviews12 <- url12%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>% 
    gsub("\\n", "", .)

reviews12.1 <- url12.1%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>% 
    gsub("\\n", "", .)

reviews12.2 <- url12.2%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>%
    gsub("\\n", "", .)

reviews12.3 <- url12.3%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text()  %>%
    gsub("\\n", "", .)
reviews12.3 <- reviews12.3[1:12]   

reviews12.4 <- url12.4%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text()  %>%
    gsub("\\n", "", .)
reviews12.4 <- reviews12.4[1:10]

#Data Frames
dataname12 <- data.frame(
    ReviewerName = c(names12, names12.1, names12.2, names12.3)[1:50]
)

datapurchaseType12 <- data.frame(
    TypeOfPurchase = c(purchasetype12, purchasetype12.1, purchasetype12.2, purchasetype12.3, purchasetype12.4)[1:50]
)

dataDate12 <- data.frame(
    Date = c(daterev12, daterev12.1, daterev12.2, daterev12.3)[1:50]
)

rate12 <- data.frame(
    IndividualRating = c(rates12, rates12.1, rates12.2, rates12.3)[1:50]
)

review_dataframe12 <- data.frame(
    ReviewText = c(reviews12, reviews12.1, reviews12.2, reviews12.3, reviews12.4)[1:50]
) 

pro12 <- rep(subset24products[12], 50)

combinedProducts12 <- data.frame( 
    Product = pro12,
    ReviewerName = dataname12$ReviewerName,
    TypeOfPurchase = datapurchaseType12$TypeOfPurchase,
    Date = dataDate12$Date,
    IndividualRating = rate12$IndividualRating,
    ReviewText = review_dataframe12$ReviewText
)
combinedProducts12

#Product 12 Reviews
write.csv(combinedProducts12, file = "12thProducts.csv")
```
Product 13
```{r} 
URL13 <- "https://www.amazon.com.au/product-reviews/B0C73X3P8B/ref=acr_search_hist_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews#reviews-filter-bar"
session <- bow(URL13, user_agent = "Educational Purposes")
session

url13 <- read_html(URL13)

URL13.1 <- "https://www.amazon.com.au/product-reviews/B0C73X3P8B/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=2#reviews-filter-bar"
session <- bow(URL13.1, user_agent = "Educational Purposes")
session

url13.1 <- read_html(URL13.1)

URL13.2 <- "https://www.amazon.com.au/product-reviews/B0C73X3P8B/ref=cm_cr_arp_d_paging_btm_next_3?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=3#reviews-filter-bar"
session <- bow(URL13.2, user_agent = "Educational Purposes")
session

url13.2 <- read_html(URL13.2)

URL13.3 <- "https://www.amazon.com.au/product-reviews/B0C73X3P8B/ref=cm_cr_arp_d_paging_btm_next_4?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=4#reviews-filter-bar"
session <- bow(URL13.3, user_agent = "Educational Purposes")
session

url13.3 <- read_html(URL13.3)

URL13.4 <- "https://www.amazon.com.au/product-reviews/B0C73X3P8B/ref=cm_cr_arp_d_paging_btm_next_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=5#reviews-filter-bar"
url13.4 <- read_html(URL13.4)
```
Product 13
```{r}
names13 <- url13%>%
    html_nodes("div.a-profile-content") %>%
    html_text() 
names13

names13.1 <- url13.1%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names13.1 <- names13.1[3:11] 
names13.1

names13.2 <- url13.2%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names13.2 <- names13.2[3:9] 
names13.2

names13.3 <- url13.3%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names13.3 <- names13.3[3:12]
names13.3

#Type of purchase 
purchasetype13 <- url13%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype13.1 <- url13.1%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype13.2 <- url13.2%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()
 
purchasetype13.3 <- url13.3%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype13.4 <- url13.4%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

#Date of Review 
daterev13 <- url13%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev13.1 <- url13.1%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev13.2 <- url13.2%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev13.3 <- url13.3%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev13.4 <- url13.4%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

#Subset
daterevs13.3 <- daterev13.4[1:20]

#Individual Ratings 
rates13 <- url13%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates13.1 <- url13.1%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates13.2 <- url13.2%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates13.3 <- url13.3%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates13.4 <- url13.4%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

#Reviews
reviews13 <- url13%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>% 
    gsub("\\n", "", .)

reviews13.1 <- url13.1%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>% 
    gsub("\\n", "", .)

reviews13.2 <- url13.2%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>%
    gsub("\\n", "", .)

reviews13.3 <- url13.3%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text()  %>%
    gsub("\\n", "", .)
reviews13.3 <- reviews13.3[1:12]   

reviews13.4 <- url13.4%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text()  %>%
    gsub("\\n", "", .)
reviews13.4 <- reviews13.4[1:10] 

#Data Frames
dataname13 <- data.frame(
    ReviewerName = c(names13, names13.1, names13.2, names13.3)[1:50]
)

datapurchaseType13 <- data.frame(
    TypeOfPurchase = c(purchasetype13, purchasetype13.1, purchasetype13.2, purchasetype13.3, purchasetype13.4)[1:50]
)

dataDate13 <- data.frame(
    Date = c(daterev13, daterev13.1, daterev13.2, daterev13.3)[1:50]
)

rate13 <- data.frame(
    IndividualRating = c(rates13, rates13.1, rates13.2, rates13.3)[1:50]
)

review_dataframe13 <- data.frame(
    ReviewText = c(reviews13, reviews13.1, reviews13.2, reviews13.3, reviews13.4)[1:50]
) 

pro13 <- rep(subset24products[13], 50)

combinedProducts13 <- data.frame( 
    Product = pro13,
    ReviewerName = dataname13$ReviewerName,
    TypeOfPurchase = datapurchaseType13$TypeOfPurchase,
    Date = dataDate13$Date,
    IndividualRating = rate13$IndividualRating,
    ReviewText = review_dataframe13$ReviewText
)
combinedProducts13

#Product 13 Reviews
write.csv(combinedProducts13, file = "13thProducts.csv")
```
Product 14
```{r}
URL14 <- "https://www.amazon.com.au/product-reviews/B0CM3GGZDZ/ref=acr_search_hist_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews#reviews-filter-bar"
session <- bow(URL14, user_agent = "Educational Purposes")
session

url14 <- read_html(URL14)

URL14.1 <- "https://www.amazon.com.au/product-reviews/B0CM3GGZDZ/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=2#reviews-filter-bar"
session <- bow(URL14.1, user_agent = "Educational Purposes")
session

url14.1 <- read_html(URL14.1)

URL14.2 <- "https://www.amazon.com.au/product-reviews/B0CM3GGZDZ/ref=cm_cr_arp_d_paging_btm_next_3?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=3#reviews-filter-bar"
session <- bow(URL14.2, user_agent = "Educational Purposes")
session

url14.2 <- read_html(URL14.2)

URL14.3 <- "https://www.amazon.com.au/product-reviews/B0CM3GGZDZ/ref=cm_cr_arp_d_paging_btm_next_4?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=4#reviews-filter-bar"
session <- bow(URL14.3, user_agent = "Educational Purposes")
session

url14.3 <- read_html(URL14.3)

URL14.4 <- "https://www.amazon.com.au/product-reviews/B0CM3GGZDZ/ref=cm_cr_arp_d_paging_btm_next_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=5#reviews-filter-bar"
url14.4 <- read_html(URL14.4)
```
Product 14
```{r}
#Reviewers Names
names14 <- url14%>%
    html_nodes("div.a-profile-content") %>%
    html_text() 
names14

names14.1 <- url14.1%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names14.1 <- names14.1[3:11] 
names14.1

names14.2 <- url14.2%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names14.2 <- names14.2[3:9] 
names14.2

names14.3 <- url14.3%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names14.3 <- names14.3[3:12]
names14.3

#Type of Purchase 
purchasetype14 <- url14%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype14.1 <- url14.1%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype14.2 <- url14.2%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype14.3 <- url14.3%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype14.4 <- url14.4%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

#Date of Review
daterev14 <- url14%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev14.1 <- url14.1%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev14.2 <- url14.2%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev14.3 <- url14.3%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev14.4 <- url14.4%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

#Subset
daterevs14.3 <- daterev14.4[1:20]

#Individual Ratings 
rates14 <- url14%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates14.1 <- url14.1%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()
 
rates14.2 <- url14.2%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()
 
rates14.3 <- url14.3%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates14.4 <- url14.4%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

#Review
reviews14 <- url14%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>% 
    gsub("\\n", "", .)

reviews14.1 <- url14.1%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>% 
    gsub("\\n", "", .)

reviews14.2 <- url14.2%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>%
    gsub("\\n", "", .)

reviews14.3 <- url14.3%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text()  %>%
    gsub("\\n", "", .)
reviews14.3 <- reviews14.3[1:12]   

reviews14.4 <- url14.4%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text()  %>%
    gsub("\\n", "", .)
reviews14.4 <- reviews14.4[1:10] 

#Data Frames
dataname14 <- data.frame(
    ReviewerName = c(names14, names14.1, names14.2, names14.3)[1:50]
)

datapurchaseType14 <- data.frame(
    TypeOfPurchase = c(purchasetype14, purchasetype14.1, purchasetype14.2, purchasetype14.3, purchasetype14.4)[1:50]
)

dataDate14 <- data.frame(
    Date = c(daterev14, daterev14.1, daterev14.2, daterev14.3)[1:50]
)

rate14 <- data.frame(
    IndividualRating = c(rates14, rates14.1, rates14.2, rates14.3)[1:50]
)

review_dataframe14 <- data.frame(
    ReviewText = c(reviews14, reviews14.1, reviews14.2, reviews14.3, reviews14.4)[1:50]
) 

pro14 <- rep(subset24products[14], 50)

combinedProducts14 <- data.frame( 
    Product = pro14,
    ReviewerName = dataname14$ReviewerName,
    TypeOfPurchase = datapurchaseType14$TypeOfPurchase,
    Date = dataDate14$Date,
    IndividualRating = rate14$IndividualRating,
    ReviewText = review_dataframe14$ReviewText
)
combinedProducts14

#Product 14
write.csv(combinedProducts14, file = "14thProducts.csv")
```
Product 15
```{r}
URL15 <- "https://www.amazon.com.au/product-reviews/B0C8HCSL1Z/ref=acr_search_hist_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews#reviews-filter-bar"
session <- bow(URL15, user_agent = "Educational Purposes")
session

url15 <- read_html(URL15)

URL15.1 <- "https://www.amazon.com.au/product-reviews/B0C8HCSL1Z/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=2#reviews-filter-bar"
session <- bow(URL15.1, user_agent = "Educational Purposes")
session

url15.1 <- read_html(URL15.1)

URL15.2 <- "https://www.amazon.com.au/product-reviews/B0C8HCSL1Z/ref=cm_cr_arp_d_paging_btm_next_3?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=3#reviews-filter-bar"
session <- bow(URL15.2, user_agent = "Educational Purposes")
session

url15.2 <- read_html(URL15.2)

URL15.3 <- "https://www.amazon.com.au/product-reviews/B0C8HCSL1Z/ref=cm_cr_arp_d_paging_btm_next_4?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=4#reviews-filter-bar"
session <- bow(URL15.3, user_agent = "Educational Purposes")
session

url15.3 <- read_html(URL15.3)

URL15.4 <- "https://www.amazon.com.au/product-reviews/B0C8HCSL1Z/ref=cm_cr_arp_d_paging_btm_next_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=5#reviews-filter-bar"
url15.4 <- read_html(URL15.4)
```
Product 15
```{r}
#Reviewers Names
names15 <- url15%>%
    html_nodes("div.a-profile-content") %>%
    html_text() 
names15

names15.1 <- url15.1%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names15.1 <- names15.1[3:11] 
names15.1

names15.2 <- url15.2%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names15.2 <- names15.2[3:9] 
names15.2

names15.3 <- url15.3%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names15.3 <- names15.3[3:12]
names15.3

#Type of Purchase 
purchasetype15 <- url15%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()
 
purchasetype15.1 <- url15.1%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype15.2 <- url15.2%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype15.3 <- url15.3%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype15.4 <- url15.4%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

#Date of Review
daterev15 <- url15%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev15.1 <- url15.1%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev15.2 <- url15.2%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev15.3 <- url15.3%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev15.4 <- url15.4%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

#Subset 
daterevs15.3 <- daterev15.4[1:20]

#Individual Ratings 
rates15 <- url15%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates15.1 <- url15.1%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates15.2 <- url15.2%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()
 
rates15.3 <- url15.3%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()
 
rates15.4 <- url15.4%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

#Reviews
reviews15 <- url15%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>% 
    gsub("\\n", "", .)

reviews15.1 <- url15.1%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>% 
    gsub("\\n", "", .)

reviews15.2 <- url15.2%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>%
    gsub("\\n", "", .)

reviews15.3 <- url15.3%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text()  %>%
    gsub("\\n", "", .)
reviews15.3 <- reviews15.3[1:12]   

reviews15.4 <- url15.4%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text()  %>%
    gsub("\\n", "", .)
reviews15.4 <- reviews15.4[1:10] 

#Data Frames
dataname15 <- data.frame(
    ReviewerName = c(names15, names15.1, names15.2, names15.3)[1:50]
)

datapurchaseType15 <- data.frame(
    TypeOfPurchase = c(purchasetype15, purchasetype15.1, purchasetype15.2, purchasetype15.3, purchasetype15.4)[1:50]
)

dataDate15 <- data.frame(
    Date = c(daterev15, daterev15.1, daterev15.2, daterev15.3)[1:50]
)

rate15 <- data.frame(
    IndividualRating = c(rates15, rates15.1, rates15.2, rates15.3)[1:50]
)

review_dataframe15 <- data.frame(
    ReviewText = c(reviews15, reviews15.1, reviews15.2, reviews15.3, reviews15.4)[1:50]
) 

pro15 <- rep(subset24products[15], 50)

combinedProducts15 <- data.frame( 
    Product = pro15,
    ReviewerName = dataname15$ReviewerName,
    TypeOfPurchase = datapurchaseType15$TypeOfPurchase,
    Date = dataDate15$Date,
    IndividualRating = rate15$IndividualRating,
    ReviewText = review_dataframe15$ReviewText
)
combinedProducts15

#Product 15 csv
write.csv(combinedProducts15, file = "15thProducts.csv")
``` 
Product 16
```{r}
URL16 <- "https://www.amazon.com.au/product-reviews/B0CD158GTP/ref=acr_search_hist_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews#reviews-filter-bar"
session <- bow(URL16, user_agent = "Educational Purposes")
session

url16 <- read_html(URL16)

URL16.1 <- "https://www.amazon.com.au/product-reviews/B0CD158GTP/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=2#reviews-filter-bar"
session <- bow(URL16.1, user_agent = "Educational Purposes")
session

url16.1 <- read_html(URL16.1)

URL16.2 <- "https://www.amazon.com.au/product-reviews/B0CD158GTP/ref=cm_cr_arp_d_paging_btm_next_3?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=3#reviews-filter-bar"
session <- bow(URL16.2, user_agent = "Educational Purposes")
session

url16.2 <- read_html(URL16.2)

URL16.3 <- "https://www.amazon.com.au/product-reviews/B0CD158GTP/ref=cm_cr_arp_d_paging_btm_next_4?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=4#reviews-filter-bar"
session <- bow(URL16.3, user_agent = "Educational Purposes")
session

url16.3 <- read_html(URL16.3)

URL16.4 <- "https://www.amazon.com.au/product-reviews/B0CD158GTP/ref=cm_cr_arp_d_paging_btm_next_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=5#reviews-filter-bar"
url16.4 <- read_html(URL16.4)
```
Product 16
```{r}
#Reviewers Names
names16 <- url16%>%
    html_nodes("div.a-profile-content") %>%
    html_text() 
names16

names16.1 <- url16.1%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names16.1 <- names16.1[3:11] 
names16.1

names16.2 <- url16.2%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names16.2 <- names16.2[3:9] 
names16.2

names16.3 <- url16.3%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names16.3 <- names16.3[3:12]
names16.3

#Type of Purchase 
purchasetype16 <- url16%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype16.1 <- url16.1%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype16.2 <- url16.2%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype16.3 <- url16.3%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype16.4 <- url16.4%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

#Date of Review
daterev16 <- url16%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev16.1 <- url16.1%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev16.2 <- url16.2%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev16.3 <- url16.3%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev16.4 <- url16.4%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

#Subset
daterevs16.3 <- daterev16.4[1:20]

#Individual Ratings 
rates16 <- url16%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates16.1 <- url16.1%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates16.2 <- url16.2%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

#Individual Ratings 
rates16.3 <- url16.3%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates16.4 <- url16.4%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

#Reviews
reviews16 <- url16%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>% 
    gsub("\\n", "", .)

reviews16.1 <- url16.1%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>% 
    gsub("\\n", "", .)

reviews16.2 <- url16.2%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>%
    gsub("\\n", "", .)

reviews16.3 <- url16.3%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text()  %>%
    gsub("\\n", "", .)
reviews16.3 <- reviews16.3[1:12]   

reviews16.4 <- url16.4%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text()  %>%
    gsub("\\n", "", .)
reviews16.4 <- reviews16.4[1:10] 

#Data Frames
dataname16 <- data.frame(
    ReviewerName = c(names16, names16.1, names16.2, names16.3)[1:50]
)

datapurchaseType16 <- data.frame(
    TypeOfPurchase = c(purchasetype16, purchasetype16.1, purchasetype16.2, purchasetype16.3, purchasetype16.4)[1:50]
)

dataDate16 <- data.frame(
    Date = c(daterev16, daterev16.1, daterev16.2, daterev16.3)[1:50]
)

rate16 <- data.frame(
    IndividualRating = c(rates16, rates16.1, rates16.2, rates16.3)[1:50]
)

review_dataframe16 <- data.frame(
    ReviewText = c(reviews16, reviews16.1, reviews16.2, reviews16.3, reviews16.4)[1:50]
) 

pro16 <- rep(subset24products[16], 50)

combinedProducts16 <- data.frame( 
    Product = pro16,
    ReviewerName = dataname16$ReviewerName,
    TypeOfPurchase = datapurchaseType16$TypeOfPurchase,
    Date = dataDate16$Date,
    IndividualRating = rate16$IndividualRating,
    ReviewText = review_dataframe16$ReviewText
)
combinedProducts16

#Product 16 csv
write.csv(combinedProducts16, file = "16thProduct.csv")
```
Product 17
```{r}
URL17 <- "https://www.amazon.com.au/product-reviews/B00I3LUR42/ref=acr_search_hist_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews#reviews-filter-bar"
session <- bow(URL17, user_agent = "Educational Purposes")
session

url17 <- read_html(URL17)

URL17.1 <- "https://amazon.com.au/product-reviews/B00I3LUR42/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=2#reviews-filter-bar"
session <- bow(URL17.1, user_agent = "Educational Purposes")
session

url17.1 <- read_html(URL17.1)

URL17.2 <- "https://amazon.com.au/product-reviews/B00I3LUR42/ref=cm_cr_arp_d_paging_btm_next_3?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=3#reviews-filter-bar"
session <- bow(URL17.2, user_agent = "Educational Purposes")
session

url17.2 <- read_html(URL17.2)

URL17.3 <- "https://amazon.com.au/product-reviews/B00I3LUR42/ref=cm_cr_arp_d_paging_btm_next_4?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=4#reviews-filter-bar"
session <- bow(URL17.3, user_agent = "Educational Purposes")
session

url17.3 <- read_html(URL17.3)

URL17.4 <- "https://amazon.com.au/product-reviews/B00I3LUR42/ref=cm_cr_arp_d_paging_btm_next_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=5#reviews-filter-bar"
url17.4 <- read_html(URL17.4)
```
Product 17
```{r}
#Reviewers Names
names17 <- url17%>%
    html_nodes("div.a-profile-content") %>%
    html_text() 
names17

names17.1 <- url17.1%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names17.1 <- names17.1[3:11] 
names17.1

names17.2 <- url17.2%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names17.2 <- names17.2[3:9] 
names17.2

names17.3 <- url17.3%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names17.3 <- names17.3[3:12]
names17.3

#Type of purchase 
purchasetype17 <- url17%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype17.1 <- url17.1%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype17.2 <- url17.2%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype17.3 <- url17.3%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype17.4 <- url17.4%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

#Date of Review 
daterev17 <- url17%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev17.1 <- url17.1%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()
 
daterev17.2 <- url17.2%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev17.3 <- url17.3%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev17.4 <- url17.4%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

#Subset
daterevs17.3 <- daterev17.4[1:20]

#Individual Ratings 
rates17 <- url17%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates17.1 <- url17.1%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates17.2 <- url17.2%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()
 
rates17.3 <- url17.3%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates17.4 <- url17.4%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

#Reviews
reviews17 <- url17%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>% 
    gsub("\\n", "", .)

reviews17.1 <- url17.1%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>% 
    gsub("\\n", "", .)

reviews17.2 <- url17.2%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>%
    gsub("\\n", "", .)

reviews17.3 <- url17.3%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text()  %>%
    gsub("\\n", "", .)
reviews17.3 <- reviews17.3[1:12]   

reviews17.4 <- url17.4%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text()  %>%
    gsub("\\n", "", .)
reviews17.4 <- reviews17.4[1:10]

#Data Frames
dataname17 <- data.frame(
    ReviewerName = c(names17, names17.1, names17.2, names17.3)[1:50]
)

datapurchaseType17 <- data.frame(
    TypeOfPurchase = c(purchasetype17, purchasetype17.1, purchasetype17.2, purchasetype17.3, purchasetype17.4)[1:50]
)

dataDate17 <- data.frame(
    Date = c(daterev17, daterev17.1, daterev17.2, daterev17.3)[1:50]
)

rate17 <- data.frame(
    IndividualRating = c(rates17, rates17.1, rates17.2, rates17.3)[1:50]
)

review_dataframe17 <- data.frame(
    ReviewText = c(reviews17, reviews17.1, reviews17.2, reviews17.3, reviews17.4)[1:50]
) 

pro17 <- rep(subset24products[17], 50)

combinedProducts17 <- data.frame( 
    Product = pro17,
    ReviewerName = dataname17$ReviewerName,
    TypeOfPurchase = datapurchaseType17$TypeOfPurchase,
    Date = dataDate17$Date,
    IndividualRating = rate17$IndividualRating,
    ReviewText = review_dataframe17$ReviewText
)
combinedProducts17

#Product 17 csv
write.csv(combinedProducts17, file = "17thProduct.csv")
```
Product 18
```{r} 
URL18 <- "https://www.amazon.com.au/product-reviews/B07D794Y23/ref=acr_search_hist_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews#reviews-filter-bar"
session <- bow(URL18, user_agent = "Educational Purposes")
session

url18 <- read_html(URL18)

URL18.1 <- "https://www.amazon.com.au/product-reviews/B07D794Y23/ref=cm_cr_getr_d_paging_btm_next_2?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=2#reviews-filter-bar"
session <- bow(URL18.1, user_agent = "Educational Purposes")
session

url18.1 <- read_html(URL18.1)

URL18.2 <- "https://www.amazon.com.au/product-reviews/B07D794Y23/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=3#reviews-filter-bar"
session <- bow(URL18.2, user_agent = "Educational Purposes")
session

url18.2 <- read_html(URL18.2)

URL18.3 <- "https://www.amazon.com.au/product-reviews/B07D794Y23/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=4#reviews-filter-bar"
session <- bow(URL18.3, user_agent = "Educational Purposes")
session

url18.3 <- read_html(URL18.3)

URL18.4 <- "https://www.amazon.com.au/product-reviews/B07D794Y23/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=5#reviews-filter-bar"
url18.4 <- read_html(URL18.4)
```
Product 18
```{r}
#Reviewers Names
names18 <- url18%>%
    html_nodes("div.a-profile-content") %>%
    html_text() 
names18

names18.1 <- url18.1%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names18.1 <- names18.1[3:11] 
names18.1

names18.2 <- url18.2%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names18.2 <- names18.2[3:9] 
names18.2

names18.3 <- url18.3%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names18.3 <- names18.3[3:12]
names18.3

#Type of Purchase 
purchasetype18 <- url18%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype18.1 <- url18.1%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype18.2 <- url18.2%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype18.3 <- url18.3%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype18.4 <- url18.4%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

#Date of Reviews 
daterev18 <- url18%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev18.1 <- url18.1%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev18.2 <- url18.2%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev18.3 <- url18.3%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev18.4 <- url18.4%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

#Subset 
daterevs18.3 <- daterev18.4[1:20]

#Individual Ratings 
rates18 <- url18%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates18.1 <- url18.1%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates18.2 <- url18.2%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates18.3 <- url18.3%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates18.4 <- url18.4%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

#Reviews
reviews18 <- url18%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>% 
    gsub("\\n", "", .)

reviews18.1 <- url18.1%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>% 
    gsub("\\n", "", .)

reviews18.2 <- url18.2%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>%
    gsub("\\n", "", .)

reviews18.3 <- url18.3%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text()  %>%
    gsub("\\n", "", .)
reviews18.3 <- reviews18.3[1:12]   

reviews18.4 <- url18.4%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text()  %>%
    gsub("\\n", "", .)
reviews18.4 <- reviews18.4[1:10] 

#Data Frames
dataname18 <- data.frame(
    ReviewerName = c(names18, names18.1, names18.2, names18.3)[1:50]
)

datapurchaseType18 <- data.frame(
    TypeOfPurchase = c(purchasetype18, purchasetype18.1, purchasetype18.2, purchasetype18.3, purchasetype18.4)[1:50]
)

dataDate18 <- data.frame(
    Date = c(daterev18, daterev18.1, daterev18.2, daterev18.3)[1:50]
)

rate18 <- data.frame(
    IndividualRating = c(rates18, rates18.1, rates18.2, rates18.3)[1:50]
)

review_dataframe18 <- data.frame(
    ReviewText = c(reviews18, reviews18.1, reviews18.2, reviews18.3, reviews18.4)[1:50]
) 

pro18 <- rep(subset24products[18], 50)

combinedProducts18 <- data.frame( 
    Product = pro18,
    ReviewerName = dataname18$ReviewerName,
    TypeOfPurchase = datapurchaseType18$TypeOfPurchase,
    Date = dataDate18$Date,
    IndividualRating = rate18$IndividualRating,
    ReviewText = review_dataframe18$ReviewText
)

combinedProducts18

#Product 18 csv 
write.csv(combinedProducts18, file = "18thProduct.csv")
``` 
Product 19
```{r} 
URL19 <- "https://www.amazon.com.au/product-reviews/B09FSXY3Y8/ref=acr_search_hist_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews#reviews-filter-bar"
session <- bow(URL19, user_agent = "Educational Purposes")
session

url19 <- read_html(URL19)

URL19.1 <- "https://www.amazon.com.au/product-reviews/B09FSXY3Y8/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=2#reviews-filter-bar"
session <- bow(URL19.1, user_agent = "Educational Purposes")
session

url19.1 <- read_html(URL19.1)

URL19.2 <- "https://www.amazon.com.au/product-reviews/B09FSXY3Y8/ref=cm_cr_arp_d_paging_btm_next_3?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=3#reviews-filter-bar"
session <- bow(URL19.2, user_agent = "Educational Purposes")
session

url19.2 <- read_html(URL19.2)

URL19.3 <- "https://www.amazon.com.au/product-reviews/B09FSXY3Y8/ref=cm_cr_arp_d_paging_btm_next_4?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=4#reviews-filter-bar"
session <- bow(URL19.3, user_agent = "Educational Purposes")
session

url19.3 <- read_html(URL19.3)

URL19.4 <- "https://www.amazon.com.au/product-reviews/B09FSXY3Y8/ref=cm_cr_arp_d_paging_btm_next_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=5#reviews-filter-bar"
url19.4 <- read_html(URL19.4)
```
Product 19
```{r}
#Reviewers Names
names19 <- url19%>%
    html_nodes("div.a-profile-content") %>%
    html_text() 
names19

names19.1 <- url19.1%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names19.1 <- names19.1[3:11] 
names19.1

names19.2 <- url19.2%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names19.2 <- names19.2[3:9] 
names19.2

names19.3 <- url19.3%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names19.3 <- names19.3[3:12]
names19.3

#Type of Purchase 
purchasetype19 <- url19%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype19.1 <- url19.1%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype19.2 <- url19.2%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype19.3 <- url19.3%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype19.4 <- url19.4%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

#Date of Review  
daterev19 <- url19%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev19.1 <- url19.1%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev19.2 <- url19.2%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev19.3 <- url19.3%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev19.4 <- url19.4%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

#Subset
daterevs19.3 <- daterev19.4[1:20]

#Individual Ratings 
rates19 <- url19%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates19.1 <- url19.1%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates19.2 <- url19.2%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates19.3 <- url19.3%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates19.4 <- url19.4%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

#Reviews
reviews19 <- url19%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>% 
    gsub("\\n", "", .)

reviews19.1 <- url19.1%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>% 
    gsub("\\n", "", .)

reviews19.2 <- url19.2%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>%
    gsub("\\n", "", .)

reviews19.3 <- url19.3%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text()  %>%
    gsub("\\n", "", .)
reviews19.3 <- reviews19.3[1:12]   

reviews19.4 <- url19.4%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text()  %>%
    gsub("\\n", "", .)
reviews19.4 <- reviews19.4[1:10]

#Data Frames
dataname19 <- data.frame(
    ReviewerName = c(names19, names19.1, names19.2, names19.3)[1:50]
)

datapurchaseType19 <- data.frame(
    TypeOfPurchase = c(purchasetype19, purchasetype19.1, purchasetype19.2, purchasetype19.3, purchasetype19.4)[1:50]
)

dataDate19 <- data.frame(
    Date = c(daterev19, daterev19.1, daterev19.2, daterev19.3)[1:50]
)

rate19 <- data.frame(
    IndividualRating = c(rates19, rates19.1, rates19.2, rates19.3)[1:50]
)

review_dataframe19 <- data.frame(
    ReviewText = c(reviews19, reviews19.1, reviews19.2, reviews19.3, reviews19.4)[1:50]
) 

pro19 <- rep(subset24products[19], 50)

combinedProducts19 <- data.frame( 
    Product = pro19,
    ReviewerName = dataname19$ReviewerName,
    TypeOfPurchase = datapurchaseType19$TypeOfPurchase,
    Date = dataDate19$Date,
    IndividualRating = rate19$IndividualRating,
    ReviewText = review_dataframe19$ReviewText
)

combinedProducts19

#Product 19 csv
write.csv(combinedProducts19, file = "19thProduct.csv")
```
Product 20
```{r}
URL20 <- "https://www.amazon.com.au/product-reviews/B0981LVH2V/ref=acr_search_hist_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews#reviews-filter-barr"
session <- bow(URL20, user_agent = "Educational Purposes")
session

url20 <- read_html(URL20)

URL20.1 <- "https://www.amazon.com.au/product-reviews/B0981LVH2V/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=2#reviews-filter-bar"
session <- bow(URL20.1, user_agent = "Educational Purposes")
session

url20.1 <- read_html(URL20.1)

URL20.2 <- "https://www.amazon.com.au/product-reviews/B0981LVH2V/ref=cm_cr_arp_d_paging_btm_next_3?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=3#reviews-filter-bar"
session <- bow(URL20.2, user_agent = "Educational Purposes")
session

url20.2 <- read_html(URL20.2)

URL20.3 <- "https://www.amazon.com.au/product-reviews/B0981LVH2V/ref=cm_cr_arp_d_paging_btm_next_4?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=4#reviews-filter-bar"
session <- bow(URL20.3, user_agent = "Educational Purposes")
session

url20.3 <- read_html(URL20.3)

URL20.4 <- "https://www.amazon.com.au/product-reviews/B0981LVH2V/ref=cm_cr_arp_d_paging_btm_next_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=5#reviews-filter-bar"
url20.4 <- read_html(URL20.4)
```
Product 20
```{r}
#Reviewers Names
names20 <- url20%>%
    html_nodes("div.a-profile-content") %>%
    html_text() 
names20

names20.1 <- url20.1%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names20.1 <- names20.1[3:11] 
names20.1

names20.2 <- url20.2%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names20.2 <- names20.2[3:9] 
names20.2

names20.3 <- url20.3%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names20.3 <- names20.3[3:12]
names20.3

#Type of Purchase 
purchasetype20 <- url20%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype20.1 <- url20.1%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype20.2 <- url20.2%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype20.3 <- url20.3%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype20.4 <- url20.4%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

#Date of Reviews
daterev20 <- url20%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev20.1 <- url20.1%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev20.2 <- url20.2%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev20.3 <- url20.3%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev20.4 <- url20.4%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

#Subset
daterevs20.3 <- daterev20.4[1:20]

#Individual Ratings 
rates20 <- url20%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates20.1 <- url20.1%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates20.2 <- url20.2%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates20.3 <- url20.3%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates20.4 <- url20.4%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

#Reviews
reviews20 <- url20%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>% 
    gsub("\\n", "", .)

reviews20.1 <- url20.1%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>% 
    gsub("\\n", "", .)

reviews20.2 <- url20.2%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>%
    gsub("\\n", "", .)

reviews20.3 <- url20.3%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text()  %>%
    gsub("\\n", "", .)
reviews20.3 <- reviews20.3[1:12]   

reviews20.4 <- url20.4%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text()  %>%
    gsub("\\n", "", .)
reviews20.4 <- reviews20.4[1:10] 

#Data Frames
dataname20 <- data.frame(
    ReviewerName = c(names20, names20.1, names20.2, names20.3)[1:50]
)

datapurchaseType20 <- data.frame(
    TypeOfPurchase = c(purchasetype20, purchasetype20.1, purchasetype20.2, purchasetype20.3, purchasetype20.4)[1:50]
)

dataDate20 <- data.frame(
    Date = c(daterev20, daterev20.1, daterev20.2, daterev20.3)[1:50]
)

rate20 <- data.frame(
    IndividualRating = c(rates20, rates20.1, rates20.2, rates20.3)[1:50]
)

review_dataframe20 <- data.frame(
    ReviewText = c(reviews20, reviews20.1, reviews20.2, reviews20.3, reviews20.4)[1:50]
) 

pro20 <- rep(subset24products[20], 50)

combinedProducts20 <- data.frame( 
    Product = pro20,
    ReviewerName = dataname20$ReviewerName,
    TypeOfPurchase = datapurchaseType20$TypeOfPurchase,
    Date = dataDate20$Date,
    IndividualRating = rate20$IndividualRating,
    ReviewText = review_dataframe20$ReviewText
)
combinedProducts20

#Product 20 csv
write.csv(combinedProducts20, file = "20thProduct.csv")
```
Product 21 
```{r}
URL21 <- "https://www.amazon.com.au/product-reviews/B07B4PDF6K/ref=acr_search_hist_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews#reviews-filter-bar"
session <- bow(URL21, user_agent = "Educational Purposes")
session

url21 <- read_html(URL21)

URL21.1 <- "https://www.amazon.com.au/product-reviews/B07B4PDF6K/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=2#reviews-filter-bar"
session <- bow(URL21.1, user_agent = "Educational Purposes")
session

url21.1 <- read_html(URL21.1)

URL21.2 <- "https://www.amazon.com.au/product-reviews/B07B4PDF6K/ref=cm_cr_arp_d_paging_btm_next_3?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=3#reviews-filter-bar"
session <- bow(URL21.2, user_agent = "Educational Purposes")
session

url21.2 <- read_html(URL21.2)

URL21.3 <- "https://www.amazon.com.au/product-reviews/B07B4PDF6K/ref=cm_cr_arp_d_paging_btm_next_4?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=4#reviews-filter-bar"
session <- bow(URL21.3, user_agent = "Educational Purposes")
session

url21.3 <- read_html(URL21.3)

URL21.4 <- "https://www.amazon.com.au/product-reviews/B07B4PDF6K/ref=cm_cr_arp_d_paging_btm_next_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=5#reviews-filter-bar"
url21.4 <- read_html(URL21.4)
```
Product 21
```{r}
#Reviewers Names
names21 <- url21%>%
    html_nodes("div.a-profile-content") %>%
    html_text() 
names21

names21.1 <- url21.1%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names21.1 <- names21.1[3:11] 
names21.1

names21.2 <- url21.2%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names21.2 <- names21.2[3:9] 
names21.2

names21.3 <- url21.3%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names21.3 <- names21.3[3:12]
names21.3

#Type of purchase 
purchasetype21 <- url21%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype21.1 <- url21.1%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype21.2 <- url21.2%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype21.3 <- url21.3%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype21.4 <- url21.4%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

#Date of Review
daterev21 <- url21%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev21.1 <- url21.1%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev21.2 <- url21.2%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev21.3 <- url21.3%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev21.4 <- url21.4%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

#Subset 
daterevs21.3 <- daterev21.4[1:20]

#Individual Ratings 
rates21 <- url21%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates21.1 <- url21.1%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates21.2 <- url21.2%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates21.3 <- url21.3%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates21.4 <- url21.4%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

#Reviews
reviews21 <- url21%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>% 
    gsub("\\n", "", .)

reviews21.1 <- url21.1%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>% 
    gsub("\\n", "", .)

reviews21.2 <- url21.2%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>%
    gsub("\\n", "", .)

reviews21.3 <- url21.3%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text()  %>%
    gsub("\\n", "", .)
reviews21.3 <- reviews21.3[1:12]   

reviews21.4 <- url21.4%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text()  %>%
    gsub("\\n", "", .)
reviews21.4 <- reviews21.4[1:10] 

#Data Frames
dataname21 <- data.frame(
    ReviewerName = c(names21, names21.1, names21.2, names21.3)[1:50]
)

datapurchaseType21 <- data.frame(
    TypeOfPurchase = c(purchasetype21, purchasetype21.1, purchasetype21.2, purchasetype21.3, purchasetype21.4)[1:50]
)

dataDate21 <- data.frame(
    Date = c(daterev21, daterev21.1, daterev21.2, daterev21.3)[1:50]
)

rate21 <- data.frame(
    IndividualRating = c(rates21, rates21.1, rates21.2, rates21.3)[1:50]
)

review_dataframe21 <- data.frame(
    ReviewText = c(reviews21, reviews21.1, reviews21.2, reviews21.3, reviews21.4)[1:50]
) 

pro21 <- rep(subset24products[21], 50)

combinedProducts21 <- data.frame( 
    Product = pro21,
    ReviewerName = dataname21$ReviewerName,
    TypeOfPurchase = datapurchaseType21$TypeOfPurchase,
    Date = dataDate21$Date,
    IndividualRating = rate21$IndividualRating,
    ReviewText = review_dataframe21$ReviewText
)
combinedProducts21

#Product 21 csv
write.csv(combinedProducts21, file = "21stProduct.csv")
```
Product 22
```{r}
URL22 <- "https://www.amazon.com.au/product-reviews/B07B4PDF6K/ref=acr_search_hist_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews#reviews-filter-bar"
session <- bow(URL22, user_agent = "Educational Purposes")
session

url22 <- read_html(URL22)

URL22.1 <- "https://www.amazon.com.au/product-reviews/B07B4PDF6K/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=2#reviews-filter-bar"
session <- bow(URL22.1, user_agent = "Educational Purposes")
session

url22.1 <- read_html(URL22.1)

URL22.2 <- "https://www.amazon.com.au/product-reviews/B07B4PDF6K/ref=cm_cr_arp_d_paging_btm_next_3?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=3#reviews-filter-bar"

session <- bow(URL22.2, user_agent = "Educational Purposes")
session

url22.2 <- read_html(URL22.2)

URL22.3 <- "https://www.amazon.com.au/product-reviews/B07B4PDF6K/ref=cm_cr_arp_d_paging_btm_next_4?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=4#reviews-filter-bar"
session <- bow(URL22.3, user_agent = "Educational Purposes")
session

url22.3 <- read_html(URL22.3)

URL22.4 <- "https://www.amazon.com.au/product-reviews/B07B4PDF6K/ref=cm_cr_arp_d_paging_btm_next_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=5#reviews-filter-bar"
url22.4 <- read_html(URL22.4)
```
Product 22
```{r}
#Reviewers Names
names22 <- url22%>%
    html_nodes("div.a-profile-content") %>%
    html_text() 
names22

names22.1 <- url22.1%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names22.1 <- names22.1[3:11] 
names22.1

names22.2 <- url22.2%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names22.2 <- names22.2[3:9] 
names22.2

names22.3 <- url22.3%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names22.3 <- names22.3[3:12]
names22.3

#Type of Purchase 
purchasetype22 <- url22%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype22.1 <- url22.1%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype22.2 <- url22.2%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype22.3 <- url22.3%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype22.4 <- url22.4%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

#Date of Review 
daterev22 <- url22%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev22.1 <- url22.1%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev22.2 <- url22.2%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev22.3 <- url22.3%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev22.4 <- url22.4%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

#Subset 
daterevs22.3 <- daterev22.4[1:20]

#Individual Ratings 
rates22 <- url22%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates22.1 <- url22.1%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates22.2 <- url22.2%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates22.3 <- url22.3%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates22.4 <- url22.4%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

#Reviews
reviews22 <- url22%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>% 
    gsub("\\n", "", .)

reviews22.1 <- url22.1%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>% 
    gsub("\\n", "", .)

reviews22.2 <- url22.2%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>%
    gsub("\\n", "", .)

reviews22.3 <- url22.3%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text()  %>%
    gsub("\\n", "", .)
reviews22.3 <- reviews22.3[1:12]   

reviews22.4 <- url22.4%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text()  %>%
    gsub("\\n", "", .)
reviews22.4 <- reviews22.4[1:10]

#Data Frames
dataname22 <- data.frame(
    ReviewerName = c(names22, names22.1, names22.2, names22.3)[1:50]
)

datapurchaseType22 <- data.frame(
    TypeOfPurchase = c(purchasetype22, purchasetype22.1, purchasetype22.2, purchasetype22.3, purchasetype22.4)[1:50]
)

dataDate22 <- data.frame(
    Date = c(daterev22, daterev22.1, daterev22.2, daterev22.3)[1:50]
)

rate22 <- data.frame(
    IndividualRating = c(rates22, rates22.1, rates22.2, rates22.3)[1:50]
)

review_dataframe22 <- data.frame(
    ReviewText = c(reviews22, reviews22.1, reviews22.2, reviews22.3, reviews22.4)[1:50]
) 

pro22 <- rep(subset24products[22], 50)

combinedProducts22 <- data.frame( 
    Product = pro22,
    ReviewerName = dataname22$ReviewerName,
    TypeOfPurchase = datapurchaseType22$TypeOfPurchase,
    Date = dataDate22$Date,
    IndividualRating = rate22$IndividualRating,
    ReviewText = review_dataframe22$ReviewText
)

combinedProducts22

#Product 22 csv
write.csv(combinedProducts22, file = "22ndProduct.csv")
head(combinedProducts22)
```
Product 23
```{r}
URL23 <- "https://www.amazon.com.au/product-reviews/B08DCLRYWB/ref=acr_search_hist_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews#reviews-filter-bar"
session <- bow(URL23, user_agent = "Educational Purposes")
session

url23 <- read_html(URL23)

URL23.1 <- "https://www.amazon.com.au/product-reviews/B08DCLRYWB/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=2#reviews-filter-bar"
session <- bow(URL23.1, user_agent = "Educational Purposes")
session

url23.1 <- read_html(URL23.1)

URL23.2 <- "https://www.amazon.com.au/product-reviews/B0CFXWNPP2/ref=acr_search_hist_4?ie=UTF8&filterByStar=four_star&reviewerType=all_reviews#reviews-filter-bar"
session <- bow(URL23.2, user_agent = "Educational Purposes")
session

url23.2 <- read_html(URL23.2)

URL23.3 <- "https://www.amazon.com.au/product-reviews/B08DCLRYWB/ref=cm_cr_arp_d_paging_btm_next_3?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=3#reviews-filter-bar"
session <- bow(URL23.3, user_agent = "Educational Purposes")
session

url23.3 <- read_html(URL23.3)

URL23.4 <- "https://www.amazon.com.au/product-reviews/B08DCLRYWB/ref=cm_cr_arp_d_paging_btm_next_4?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=4#reviews-filter-bar"
url23.4 <- read_html(URL23.4)
```
Product 24
```{r}
#Reviewers Names
names23 <- url23%>%
    html_nodes("div.a-profile-content") %>%
    html_text() 
names23

names23.1 <- url23.1%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names23.1 <- names23.1[3:11] 
names23.1

names23.2 <- url23.2%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names23.2 <- names23.2[3:9] 
names23.2

names23.3 <- url23.3%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names23.3 <- names23.3[3:12]
names23.3

#Type of Purchase 
purchasetype23 <- url23%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()
 
purchasetype23.1 <- url23.1%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype23.2 <- url23.2%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype23.3 <- url23.3%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype23.4 <- url23.4%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

#Date of Purchase
daterev23 <- url23%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev23.1 <- url23.1%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev23.2 <- url23.2%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev23.3 <- url23.3%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev23.4 <- url23.4%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

#Subset
daterevs23.3 <- daterev23.4[1:20]

#Individual Ratings 
rates23 <- url23%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates23.1 <- url23.1%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates23.2 <- url23.2%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates23.3 <- url23.3%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates23.4 <- url23.4%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

#Reviews
reviews23 <- url23%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>% 
    gsub("\\n", "", .)

reviews23.1 <- url23.1%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>% 
    gsub("\\n", "", .)

reviews23.2 <- url23.2%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>%
    gsub("\\n", "", .)

reviews23.3 <- url23.3%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text()  %>%
    gsub("\\n", "", .)
reviews23.3 <- reviews23.3[1:12]   

reviews23.4 <- url23.4%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text()  %>%
    gsub("\\n", "", .)
reviews23.4 <- reviews23.4[1:10]

#Data Frames
dataname23 <- data.frame(
    ReviewerName = c(names23, names23.1, names23.2, names23.3)[1:50]
)

datapurchaseType23 <- data.frame(
    TypeOfPurchase = c(purchasetype23, purchasetype23.1, purchasetype23.2, purchasetype23.3, purchasetype23.4)[1:50]
)

dataDate23 <- data.frame(
    Date = c(daterev23, daterev23.1, daterev23.2, daterev23.3)[1:50]
)

rate23 <- data.frame(
    IndividualRating = c(rates23, rates23.1, rates23.2, rates23.3)[1:50]
)

review_dataframe23 <- data.frame(
    ReviewText = c(reviews23, reviews23.1, reviews23.2, reviews23.3, reviews23.4)[1:50]
) 

pro23 <- rep(subset24products[23], 50)

combinedProducts23 <- data.frame( 
    Product = pro23,
    ReviewerName = dataname23$ReviewerName,
    TypeOfPurchase = datapurchaseType23$TypeOfPurchase,
    Date = dataDate23$Date,
    IndividualRating = rate23$IndividualRating,
    ReviewText = review_dataframe23$ReviewText
)
combinedProducts23

#Product 23
write.csv(combinedProducts23, file = "23rdProduct.csv")
head(combinedProducts23)
```
Product 24
```{r}
URL24 <- "https://www.amazon.com.au/product-reviews/B0CMZVZPCF/ref=acr_search_hist_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews#reviews-filter-bar"
session <- bow(URL24, user_agent = "Educational Purposes")
session

url24 <- read_html(URL24)

URL24.1 <- "https://www.amazon.com.au/product-reviews/B0CMZVZPCF/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=2#reviews-filter-bar"
session <- bow(URL24.1, user_agent = "Educational Purposes")
session

url24.1 <- read_html(URL24.1)

URL24.2 <- "https://www.amazon.com.au/product-reviews/B0CMZVZPCF/ref=cm_cr_arp_d_paging_btm_next_3?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=3#reviews-filter-bar"
session <- bow(URL24.2, user_agent = "Educational Purposes")
session

url24.2 <- read_html(URL24.2)

URL24.3 <- "https://www.amazon.com.au/product-reviews/B0CMZVZPCF/ref=cm_cr_arp_d_paging_btm_next_4?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=4#reviews-filter-bar"
session <- bow(URL24.3, user_agent = "Educational Purposes")
session

url24.3 <- read_html(URL24.3)

URL24.4 <- "https://www.amazon.com.au/product-reviews/B0CMZVZPCF/ref=cm_cr_arp_d_paging_btm_next_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=5#reviews-filter-bar"
url24.4 <- read_html(URL24.4)
```
Product 24
```{r}
#Reviewers Names
names24 <- url24%>%
    html_nodes("div.a-profile-content") %>%
    html_text() 
names24

names24.1 <- url24.1%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names24.1 <- names24.1[3:11] 
names24.1

names24.2 <- url24.2%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names24.2 <- names24.2[3:9] 
names24.2

names24.3 <- url24.3%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names24.3 <- names24.3[3:12]
names24.3

#Type of Purchase 
purchasetype24 <- url24%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()
 
purchasetype24.1 <- url24.1%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype24.2 <- url24.2%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype24.3 <- url24.3%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype24.4 <- url24.4%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

#Date of Purchase 
daterev24 <- url24%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev24.1 <- url24.1%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev24.2 <- url24.2%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev24.3 <- url24.3%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev24.4 <- url24.4%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

#Subset
daterevs24.3 <- daterev24.4[1:20]

#Individual Ratings
rates24 <- url24%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates24.1 <- url24.1%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates24.2 <- url24.2%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates24.3 <- url24.3%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates24.4 <- url24.4%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

#Reviews
reviews24 <- url24%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>% 
    gsub("\\n", "", .)

reviews24.1 <- url24.1%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>% 
    gsub("\\n", "", .)

reviews24.2 <- url24.2%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>%
    gsub("\\n", "", .)

reviews24.3 <- url24.3%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text()  %>%
    gsub("\\n", "", .)
reviews24.3 <- reviews24.3[1:12]   

reviews24.4 <- url24.4%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text()  %>%
    gsub("\\n", "", .)
reviews24.4 <- reviews24.4[1:10]

#Data Frames
dataname24 <- data.frame(
    ReviewerName = c(names24, names24.1, names24.2, names24.3)[1:50]
)

datapurchaseType24 <- data.frame(
    TypeOfPurchase = c(purchasetype24, purchasetype24.1, purchasetype24.2, purchasetype24.3, purchasetype24.4)[1:50]
)

dataDate24 <- data.frame(
    Date = c(daterev24, daterev24.1, daterev24.2, daterev24.3)[1:50]
)

rate24 <- data.frame(
    IndividualRating = c(rates24, rates24.1, rates24.2, rates24.3)[1:50]
)

review_dataframe24 <- data.frame(
    ReviewText = c(reviews24, reviews24.1, reviews24.2, reviews24.3, reviews24.4)[1:50]
) 

pro24 <- rep(subset24products[24], 50)

combinedProducts24 <- data.frame( 
    Product = pro24,
    ReviewerName = dataname24$ReviewerName,
    TypeOfPurchase = datapurchaseType24$TypeOfPurchase,
    Date = dataDate24$Date,
    IndividualRating = rate24$IndividualRating,
    ReviewText = review_dataframe24$ReviewText
)
combinedProducts24

#Product 24
write.csv(combinedProducts24, file = "24thProduct.csv")
head(combinedProducts24)
```
PRODUCT 25
```{r}
URL25 <- "https://www.amazon.com.au/product-reviews/B09CGM6FJ7/ref=acr_search_hist_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews#reviews-filter-bar"
session <- bow(URL25, user_agent = "Educational Purposes")
session

url25 <- read_html(URL25)

URL25.1 <- "https://www.amazon.com.au/product-reviews/B09CGM6FJ7/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=2#reviews-filter-bar"
session <- bow(URL25.1, user_agent = "Educational Purposes")
session

url25.1 <- read_html(URL25.1)

URL25.2 <- "https://www.amazon.com.au/product-reviews/B09CGM6FJ7/ref=cm_cr_arp_d_paging_btm_next_3?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=3#reviews-filter-bar"
session <- bow(URL25.2, user_agent = "Educational Purposes")
session

url25.2 <- read_html(URL25.2)

URL25.3 <- "https://www.amazon.com.au/product-reviews/B09CGM6FJ7/ref=cm_cr_arp_d_paging_btm_next_4?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=4#reviews-filter-bar"
session <- bow(URL25.3, user_agent = "Educational Purposes")
session

url25.3 <- read_html(URL25.3)

URL25.4 <- "https://www.amazon.com.au/product-reviews/B09CGM6FJ7/ref=cm_cr_arp_d_paging_btm_next_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=5#reviews-filter-bar"
url25.4 <- read_html(URL25.4)
```
Product 25
```{r}
#Reviewers Names
names25 <- url25%>%
    html_nodes("div.a-profile-content") %>%
    html_text() 
names25

names25.1 <- url25.1%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names25.1 <- names25.1[3:11] 
names25.1

names25.2 <- url25.2%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names25.2 <- names25.2[3:9] 
names25.2

names25.3 <- url25.3%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names25.3 <- names25.3[3:12]
names25.3

#Type of Purchase 
purchasetype25 <- url25%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype25.1 <- url25.1%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype25.2 <- url25.2%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype25.3 <- url25.3%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype25.4 <- url25.4%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

#Date of Purchase  
daterev25 <- url25%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev25.1 <- url25.1%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev25.2 <- url25.2%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev25.3 <- url25.3%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev25.4 <- url25.4%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

#Subset 
daterevs25.3 <- daterev25.4[1:20]

#Individual Ratings 
rates25 <- url25%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates25.1 <- url25.1%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates25.2 <- url25.2%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates25.3 <- url25.3%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates25.4 <- url25.4%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

#Reviews 
reviews25 <- url25%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>% 
    gsub("\\n", "", .)

reviews25.1 <- url25.1%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>% 
    gsub("\\n", "", .)

reviews25.2 <- url25.2%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>%
    gsub("\\n", "", .)

reviews25.3 <- url25.3%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text()  %>%
    gsub("\\n", "", .)
reviews25.3 <- reviews25.3[1:12]   

reviews25.4 <- url25.4%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text()  %>%
    gsub("\\n", "", .)
reviews25.4 <- reviews25.4[1:10] 

# Data Frames
dataname25 <- data.frame(
    ReviewerName = c(names25, names25.1, names25.2, names25.3)[1:50]
)

datapurchaseType25 <- data.frame(
    TypeOfPurchase = c(purchasetype25, purchasetype25.1, purchasetype25.2, purchasetype25.3, purchasetype25.4)[1:50]
)

dataDate25 <- data.frame(
    Date = c(daterev25, daterev25.1, daterev25.2, daterev25.3)[1:50]
)

rate25 <- data.frame(
    IndividualRating = c(rates25, rates25.1, rates25.2, rates25.3)[1:50]
)

review_dataframe25 <- data.frame(
    ReviewText = c(reviews25, reviews25.1, reviews25.2, reviews25.3, reviews25.4)[1:50]
) 

pro25 <- rep(subset24products[1], 50)

combinedProducts25 <- data.frame( 
    Product = pro25,
    ReviewerName = dataname25$ReviewerName,
    TypeOfPurchase = datapurchaseType25$TypeOfPurchase,
    Date = dataDate25$Date,
    IndividualRating = rate25$IndividualRating,
    ReviewText = review_dataframe25$ReviewText
)

combinedProducts25

#Product 25
write.csv(combinedProducts25, file = "25thProduct.csv")
head(combinedProducts25)
```
Product 26
```{r}
URL26 <- "https://www.amazon.com.au/product-reviews/B084ZL7T9H/ref=acr_search_hist_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews#reviews-filter-bar"
session <- bow(URL26, user_agent = "Educational Purposes")
session

url26 <- read_html(URL26)

URL26.1 <- "https://www.amazon.com.au/product-reviews/B084ZL7T9H/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=2#reviews-filter-bar"
session <- bow(URL26.1, user_agent = "Educational Purposes")
session

url26.1 <- read_html(URL26.1)

URL26.2 <- "https://www.amazon.com.au/product-reviews/B084ZL7T9H/ref=cm_cr_arp_d_paging_btm_next_3?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=3#reviews-filter-bar"
session <- bow(URL26.2, user_agent = "educational purposes")
session

url26.2 <- read_html(URL26.2)

URL26.3 <- "https://www.amazon.com.au/product-reviews/B084ZL7T9H/ref=cm_cr_arp_d_paging_btm_next_4?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=4#reviews-filter-bar"
session <- bow(URL26.3, user_agent = "Educational Purposes")
session

url26.3 <- read_html(URL26.3)

URL26.4 <- "https://www.amazon.com.au/product-reviews/B084ZL7T9H/ref=cm_cr_arp_d_paging_btm_next_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=5#reviews-filter-bar"
url26.4 <- read_html(URL26.4)
```
Product 26
```{r}
#Reviewers Names
names26 <- url26%>%
    html_nodes("div.a-profile-content") %>%
    html_text() 
names26

names26.1 <- url26.1%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names26.1 <- names26.1[3:11] 
names26.1

names26.2 <- url26.2%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names26.2 <- names26.2[3:9] 
names26.2

names26.3 <- url26.3%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names26.3 <- names26.3[3:12]
names26.3

#Type of purchase 
purchasetype26 <- url26%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype26.1 <- url26.1%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype26.2 <- url26.2%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype26.3 <- url26.3%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype26.4 <- url26.4%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

#Date of Purchase 
daterev26 <- url26%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev26.1 <- url26.1%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev26.2 <- url26.2%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev26.3 <- url26.3%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev26.4 <- url26.4%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

#Subset
daterevs26.3 <- daterev26.4[1:20]

#Individual Ratings 
rates26 <- url26%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates26.1 <- url26.1%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates26.2 <- url26.2%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates26.3 <- url26.3%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates26.4 <- url26.4%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

#Reviews
reviews26 <- url26%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>% 
    gsub("\\n", "", .)

reviews26.1 <- url26.1%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>% 
    gsub("\\n", "", .)

reviews26.2 <- url26.2%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>%
    gsub("\\n", "", .)

reviews26.3 <- url26.3%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text()  %>%
    gsub("\\n", "", .)
reviews26.3 <- reviews26.3[1:12]   

reviews26.4 <- url26.4%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text()  %>%
    gsub("\\n", "", .)
reviews26.4 <- reviews26.4[1:10]

#Data Frames
dataname26 <- data.frame(
    ReviewerName = c(names26, names26.1, names26.2, names26.3)[1:50]
)

datapurchaseType26 <- data.frame(
    TypeOfPurchase = c(purchasetype26, purchasetype26.1, purchasetype26.2, purchasetype26.3, purchasetype26.4)[1:50]
)

dataDate26 <- data.frame(
    Date = c(daterev26, daterev26.1, daterev26.2, daterev26.3)[1:50]
)

rate26 <- data.frame(
    IndividualRating = c(rates26, rates26.1, rates26.2, rates26.3)[1:50]
)

review_dataframe26 <- data.frame(
    ReviewText = c(reviews26, reviews26.1, reviews26.2, reviews26.3, reviews26.4)[1:50]
) 

pro26 <- rep(subset24products[2], 50)

combinedProducts26 <- data.frame( 
    Product = pro26,
    ReviewerName = dataname26$ReviewerName,
    TypeOfPurchase = datapurchaseType26$TypeOfPurchase,
    Date = dataDate26$Date,
    IndividualRating = rate26$IndividualRating,
    ReviewText = review_dataframe26$ReviewText
)
combinedProducts26

#Product 26 csv
write.csv(combinedProducts26, file = "26thProduct.csv") 
head(combinedProducts26)
```
Product 27
```{r}
URL27 <- "https://www.amazon.com.au/product-reviews/B0BM45DCQV/ref=acr_search_hist_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews#reviews-filter-bar"
session <- bow(URL27, user_agent = "Educational Purposes")
session

url27 <- read_html(URL27)

URL27.1 <- "https://www.amazon.com.au/product-reviews/B0BM45DCQV/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=2#reviews-filter-bar"
session <- bow(URL27.1, user_agent = "Educational Purposes")
session

url27.1 <- read_html(URL27.1)

URL27.2 <- "https://www.amazon.com.au/product-reviews/B0BM45DCQV/ref=cm_cr_arp_d_paging_btm_next_3?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=3#reviews-filter-bar"
session <- bow(URL27.2, user_agent = "Educational Purposes")
session

url27.2 <- read_html(URL27.2)

URL27.3 <- "https://www.amazon.com.au/product-reviews/B0BM45DCQV/ref=cm_cr_arp_d_paging_btm_next_4?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=4#reviews-filter-bar"
session <- bow(URL27.3, user_agent = "Educational Purposes")
session

url27.3 <- read_html(URL27.3)

URL27.4 <- "https://www.amazon.com.au/product-reviews/B0BM45DCQV/ref=cm_cr_arp_d_paging_btm_next_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=5#reviews-filter-bar"
url27.4 <- read_html(URL27.4)
```
Product 27 
```{r}
#Reviewers Names
names27 <- url27%>%
    html_nodes("div.a-profile-content") %>%
    html_text() 
names27

names27.1 <- url27.1%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names27.1 <- names27.1[3:11] 
names27.1

names27.2 <- url27.2%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names27.2 <- names27.2[3:9] 
names27.2

names27.3 <- url27.3%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names27.3 <- names27.3[3:12]
names27.3

#Type of Purchase 
purchasetype27 <- url27%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype27.1 <- url27.1%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype27.2 <- url27.2%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype27.3 <- url27.3%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype27.4 <- url27.4%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

#Date of Purchase 
daterev27 <- url27%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev27.1 <- url27.1%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev27.2 <- url27.2%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev27.3 <- url27.3%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev27.4 <- url27.4%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

#Subset 
daterevs27.3 <- daterev27.4[1:20]

#Individual Ratings 
rates27 <- url27%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()
 
rates27.1 <- url27.1%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates27.2 <- url27.2%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates27.3 <- url27.3%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates27.4 <- url27.4%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

#Reviews
reviews27 <- url27%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>% 
    gsub("\\n", "", .)

reviews27.1 <- url27.1%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>% 
    gsub("\\n", "", .)

reviews27.2 <- url27.2%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>%
    gsub("\\n", "", .)

reviews27.3 <- url27.3%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text()  %>%
    gsub("\\n", "", .)
reviews27.3 <- reviews27.3[1:12]   

reviews27.4 <- url27.4%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text()  %>%
    gsub("\\n", "", .)
reviews27.4 <- reviews27.4[1:10]


#Data Frames
dataname27 <- data.frame(
    ReviewerName = c(names27, names27.1, names27.2, names27.3)[1:50]
)

datapurchaseType27 <- data.frame(
    TypeOfPurchase = c(purchasetype27, purchasetype27.1, purchasetype27.2, purchasetype27.3, purchasetype27.4)[1:50]
)

dataDate27 <- data.frame(
    Date = c(daterev27, daterev27.1, daterev27.2, daterev27.3)[1:50]
)

rate27 <- data.frame(
    IndividualRating = c(rates27, rates27.1, rates27.2, rates27.3)[1:50]
)

review_dataframe27 <- data.frame(
    ReviewText = c(reviews27, reviews27.1, reviews27.2, reviews27.3, reviews27.4)[1:50]
) 

pro27 <- rep(subset24products2[3], 50)

combinedProducts27 <- data.frame( 
    Product = pro27,
    ReviewerName = dataname27$ReviewerName,
    TypeOfPurchase = datapurchaseType27$TypeOfPurchase,
    Date = dataDate27$Date,
    IndividualRating = rate27$IndividualRating,
    ReviewText = review_dataframe27$ReviewText
)
combinedProducts27

#Product 27 csv
write.csv(combinedProducts27, file = "27thProduct.csv")
head(combinedProducts27)
```
Product 28
```{r}
URL28 <- "https://www.amazon.com.au/product-reviews/B0CFXWNPP2/ref=acr_search_hist_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews#reviews-filter-bar"
session <- bow(URL28, user_agent = "Educational Purposes")
session

url28 <- read_html(URL28)

URL28.1 <- "https://www.amazon.com.au/product-reviews/B0CFXWNPP2/ref=acr_search_hist_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews#reviews-filter-bar"
session <- bow(URL28.1, user_agent = "Educational Purposes")
session

url28.1 <- read_html(URL28.1)

URL28.2 <- "https://www.amazon.com.au/product-reviews/B0CFXWNPP2/ref=acr_search_hist_4?ie=UTF8&filterByStar=four_star&reviewerType=all_reviews#reviews-filter-bar"
session <- bow(URL28.2, user_agent = "Educational Purposes")
session

url28.2 <- read_html(URL28.2)

URL28.3 <- "https://www.amazon.com.au/product-reviews/B0CFXWNPP2/ref=acr_search_hist_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews#reviews-filter-bar"
session <- bow(URL28.3, user_agent = "Educational Purposes")
session

url28.3 <- read_html(URL28.3)

URL28.4 <- "https://www.amazon.com.au/product-reviews/B0CFXWNPP2/ref=acr_search_hist_3?ie=UTF8&filterByStar=three_star&reviewerType=all_reviews#reviews-filter-bar"
url28.4 <- read_html(URL28.4)
```
Product 28
```{r}
#Reviewers Names
names28 <- url28%>%
    html_nodes("div.a-profile-content") %>%
    html_text() 
names28

names28.1 <- url28.1%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names28.1 <- names28.1[3:11] 
names28.1

names28.2 <- url28.2%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names28.2 <- names28.2[3:9] 
names28.2

names28.3 <- url28.3%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names28.3 <- names28.3[3:12]
names28.3

#Type of Purchase 
purchasetype28 <- url28%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype28.1 <- url28.1%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype28.2 <- url28.2%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype28.3 <- url28.3%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype28.4 <- url28.4%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

#Date of Reviews
daterev28 <- url28%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev28.1 <- url28.1%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev28.2 <- url28.2%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev28.3 <- url28.3%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev28.4 <- url28.4%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

#Subset
daterevs28.3 <- daterev28.4[1:20]

#Individual Ratings 
rates28 <- url28%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates28.1 <- url28.1%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates28.2 <- url28.2%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates28.3 <- url28.3%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates28.4 <- url28.4%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

#Reviews
reviews28 <- url28%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>% 
    gsub("\\n", "", .)

reviews28.1 <- url28.1%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>% 
    gsub("\\n", "", .)

reviews28.2 <- url28.2%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>%
    gsub("\\n", "", .)

reviews28.3 <- url28.3%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text()  %>%
    gsub("\\n", "", .)
reviews28.3 <- reviews28.3[1:12]   

reviews28.4 <- url28.4%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text()  %>%
    gsub("\\n", "", .)
reviews28.4 <- reviews28.4[1:10]

#Data Frames
dataname28 <- data.frame(
    ReviewerName = c(names28, names28.1, names28.2, names28.3)[1:50]
)

datapurchaseType28 <- data.frame(
    TypeOfPurchase = c(purchasetype28, purchasetype28.1, purchasetype28.2, purchasetype28.3, purchasetype28.4)[1:50]
)

dataDate28 <- data.frame(
    Date = c(daterev28, daterev28.1, daterev28.2, daterev28.3)[1:50]
)

rate28 <- data.frame(
    IndividualRating = c(rates28, rates28.1, rates28.2, rates28.3)[1:50]
)

review_dataframe28 <- data.frame(
    ReviewText = c(reviews28, reviews28.1, reviews28.2, reviews28.3, reviews28.4)[1:50]
) 

pro28 <- rep(subset24products2[4], 50)

combinedProducts28 <- data.frame( 
    Product = pro28,
    ReviewerName = dataname28$ReviewerName,
    TypeOfPurchase = datapurchaseType28$TypeOfPurchase,
    Date = dataDate28$Date,
    IndividualRating = rate28$IndividualRating,
    ReviewText = review_dataframe28$ReviewText
)
combinedProducts28

#Product 28 csv 
write.csv(combinedProducts28, file = "28thProduct.csv")
head(combinedProducts28)
```
Product 29
```{r}
URL29 <- "https://www.amazon.com.au/product-reviews/B09TXXG545/ref=acr_search_hist_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews#reviews-filter-bar"
session <- bow(URL29, user_agent = "Educational Purposes")
session

url29 <- read_html(URL29)

URL29.1 <- "https://www.amazon.com.au/product-reviews/B09TXXG545/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=2#reviews-filter-bar"
session <- bow(URL29.1, user_agent = "Educational Purposes")
session

url29.1 <- read_html(URL29.1)

URL29.2 <- "https://www.amazon.com.au/product-reviews/B09TXXG545/ref=cm_cr_arp_d_paging_btm_next_3?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=3#reviews-filter-bar"
session <- bow(URL29.2, user_agent = "Educational Purposes")
session

url29.2 <- read_html(URL29.2)

URL29.3 <- "https://www.amazon.com.au/product-reviews/B09TXXG545/ref=cm_cr_arp_d_paging_btm_next_4?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=4#reviews-filter-bar"
session <- bow(URL29.3, user_agent = "Educational Purposes")
session

url29.3 <- read_html(URL29.3)

URL29.4 <- "https://www.amazon.com.au/product-reviews/B09TXXG545/ref=cm_cr_arp_d_paging_btm_next_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=5#reviews-filter-bar"
url29.4 <- read_html(URL29.4)
```
Product 29
```{r}
names29 <- url29%>%
    html_nodes("div.a-profile-content") %>%
    html_text() 
names29

names29.1 <- url29.1%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names29.1 <- names29.1[3:11] 
names29.1

names29.2 <- url29.2%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names29.2 <- names29.2[3:9] 
names29.2

names29.3 <- url29.3%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names29.3 <- names29.3[3:12]
names29.3

#Type of Purchase 
purchasetype29 <- url29%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype29.1 <- url29.1%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype29.2 <- url29.2%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype29.3 <- url29.3%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype29.4 <- url29.4%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

#Date of Reviews 
daterev29 <- url29%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()
 
daterev29.1 <- url29.1%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev29.2 <- url29.2%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev29.3 <- url29.3%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev29.4 <- url29.4%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

#Subset 
daterevs29.3 <- daterev29.4[1:20]

#Individual Ratings 
rates29 <- url29%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates29.1 <- url29.1%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates29.2 <- url29.2%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()
 
rates29.3 <- url29.3%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates29.4 <- url29.4%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

#Reviews
reviews29 <- url29%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>% 
    gsub("\\n", "", .)

reviews29.1 <- url29.1%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>% 
    gsub("\\n", "", .)

reviews29.2 <- url29.2%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>%
    gsub("\\n", "", .)

reviews29.3 <- url29.3%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text()  %>%
    gsub("\\n", "", .)
reviews29.3 <- reviews29.3[1:12]   

reviews29.4 <- url29.4%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text()  %>%
    gsub("\\n", "", .)
reviews29.4 <- reviews29.4[1:10]

#Data Frames
dataname29 <- data.frame(
    ReviewerName = c(names29, names29.1, names29.2, names29.3)[1:50]
)

datapurchaseType29 <- data.frame(
    TypeOfPurchase = c(purchasetype29, purchasetype29.1, purchasetype29.2, purchasetype29.3, purchasetype29.4)[1:50]
)

dataDate29 <- data.frame(
    Date = c(daterev29, daterev29.1, daterev29.2, daterev29.3)[1:50]
)

rate29 <- data.frame(
    IndividualRating = c(rates29, rates29.1, rates29.2, rates29.3)[1:50]
)

review_dataframe29 <- data.frame(
    ReviewText = c(reviews29, reviews29.1, reviews29.2, reviews29.3, reviews29.4)[1:50]
) 

pro29 <- rep(subset24products2[5], 50)

combinedProducts29 <- data.frame( 
    Product = pro29,
    ReviewerName = dataname29$ReviewerName,
    TypeOfPurchase = datapurchaseType29$TypeOfPurchase,
    Date = dataDate29$Date,
    IndividualRating = rate29$IndividualRating,
    ReviewText = review_dataframe29$ReviewText
)

combinedProducts29

#Product 29 csv
write.csv(combinedProducts29, file = "29thProduct.csv")
head(combinedProducts29)
```
Product 30
```{r}
URL30 <- "https://www.amazon.com.au/product-reviews/B0BPMCZWJP/ref=acr_search_hist_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews#reviews-filter-bar"
session <- bow(URL30, user_agent = "Educational Purposes")
session

url30 <- read_html(URL30)

URL30.1 <- "https://www.amazon.com.au/product-reviews/B0BPMCZWJP/ref=cm_cr_getr_d_paging_btm_next_2?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=2#reviews-filter-bar"
session <- bow(URL30.1, user_agent = "Educational Purposes")
session

url30.1 <- read_html(URL30.1)

URL30.2 <- "https://www.amazon.com.au/product-reviews/B0BPMCZWJP/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=3#reviews-filter-bar"
session <- bow(URL30.2, user_agent = "Educational Purposes")
session

url30.2 <- read_html(URL30.2)

URL30.3 <- "https://www.amazon.com.au/product-reviews/B0BPMCZWJP/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=4#reviews-filter-bar"
session <- bow(URL30.3, user_agent = "Educational Purposes")
session

url30.3 <- read_html(URL30.3)

URL30.4 <- "https://www.amazon.com.au/product-reviews/B0BPMCZWJP/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=5#reviews-filter-bar"
url30.4 <- read_html(URL30.4)
```
Product 30
```{r}
#Reviewers Names
names30 <- url30%>%
    html_nodes("div.a-profile-content") %>%
    html_text() 
names30

names30.1 <- url30.1%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names30.1 <- names30.1[3:11] 
names30.1

names30.2 <- url30.2%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names30.2 <- names30.2[3:9] 
names30.2

names30.3 <- url30.3%>%
    html_nodes("div.a-profile-content") %>%
    html_text()
names30.3 <- names30.3[3:12]
names30.3

#Type of Purchase 
purchasetype30 <- url30%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype30.1 <- url30.1%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype30.2 <- url30.2%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype30.3 <- url30.3%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

purchasetype30.4 <- url30.4%>%
    html_nodes("span.a-size-mini.a-color-state.a-text-bold") %>%
    html_text()

#Date of Reviews
daterev30 <- url30%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev30.1 <- url30.1%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev30.2 <- url30.2%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev30.3 <- url30.3%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

daterev30.4 <- url30.4%>%
    html_nodes("span.a-size-base.a-color-secondary.review-date") %>%
    html_text()

#Subset
daterevs30.3 <- daterev30.4[1:20]

#Individual Ratings 
rates30 <- url30%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates30.1 <- url30.1%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates30.2 <- url30.2%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates30.3 <- url30.3%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

rates30.4 <- url30.4%>%
    html_nodes("span.a-icon-alt") %>%
    html_text()

#Reviews
reviews30 <- url30%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>% 
    gsub("\\n", "", .)

reviews30.1 <- url30.1%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>% 
    gsub("\\n", "", .)

reviews30.2 <- url30.2%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text() %>%
    gsub("\\n", "", .)

reviews30.3 <- url30.3%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text()  %>%
    gsub("\\n", "", .)
reviews30.3 <- reviews30.3[1:12]   

reviews30.4 <- url30.4%>%
    html_nodes("span.a-size-base.review-text.review-text-content") %>%
    html_text()  %>%
    gsub("\\n", "", .)
reviews30.4 <- reviews30.4[1:10]

#Data Frames
dataname30 <- data.frame(
    ReviewerName = c(names30, names30.1, names30.2, names30.3)[1:50]
)

datapurchaseType30 <- data.frame(
    TypeOfPurchase = c(purchasetype30, purchasetype30.1, purchasetype30.2, purchasetype30.3, purchasetype30.4)[1:50]
)

dataDate30 <- data.frame(
    Date = c(daterev30, daterev30.1, daterev30.2, daterev30.3)[1:50]
)

rate30 <- data.frame(
    IndividualRating = c(rates30, rates30.1, rates30.2, rates30.3)[1:50]
)

review_dataframe30 <- data.frame(
    ReviewText = c(reviews30, reviews30.1, reviews30.2, reviews30.3, reviews30.4)[1:50]
) 

pro30 <- rep(subset24products2[6], 50)

combinedProducts30 <- data.frame( 
    Product = pro30,
    ReviewerName = dataname30$ReviewerName,
    TypeOfPurchase = datapurchaseType30$TypeOfPurchase,
    Date = dataDate30$Date,
    IndividualRating = rate30$IndividualRating,
    ReviewText = review_dataframe30$ReviewText
)
combinedProducts30

#Product 30 csv 
write.csv(combinedProducts30, file = "30thProduct.csv")
head(combinedProducts30)
```
