---
title: "Lab_Exercise1"
author: "Natalie Joy Loredo"
date: "2024-02-08"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
  library(rvest)
  library(polite)
  library(httr)
  library(stringr)

url1 <- "https://www.amazon.com/Portable-Mechanical-Keyboard-MageGee-Backlit/dp/B098LG3N6R/ref=sr_1_1?_encoding=UTF8&content-id=amzn1.sym.12129333-2117-4490-9c17-6d31baf0582a&dib=eyJ2IjoiMSJ9.xPISJOYMxoc_9dHbx858f_O35VE9n8_s6WvG1ovb3cKq_CSeRgiViZDzlpzYoM86AshAE48rZlKVqrhp5CYtgi63zqI2DyCKo__fF7Vik3PLLeCQlB8QU-fCKFSY07sQLAFPVLMiQZy1rIK-42IJheLHnntBCGG05tb7MbAiQ_VT__toOsEk9FcXRswjbJpryZw3FragLIqgJTdcl4UAkRx5gcMEensmGLkqfNQBH-g.Ewv4sqhL3VCmDHjkktWJnYiJ-gfyD2ndRwLOHc0YMaM&dib_tag=se&keywords=gaming+keyboard&pd_rd_r=3891b178-b803-44e5-af31-5ce03e34ab3a&pd_rd_w=Pq9TS&pd_rd_wg=2JYj1&pf_rd_p=12129333-2117-4490-9c17-6d31baf0582a&pf_rd_r=F4AJRN21H9B3MK2W6ZY1&qid=1707956797&sr=8-1"
url2 <- "https://www.amazon.com/Redragon-S101-Keyboard-Ergonomic-Programmable/dp/B00NLZUM36/ref=sr_1_2?_encoding=UTF8&content-id=amzn1.sym.12129333-2117-4490-9c17-6d31baf0582a&dib=eyJ2IjoiMSJ9.xPISJOYMxoc_9dHbx858fyuH96vplirkkEV9nhvcubZg0TSfKqKKtaNlrROmqgkkAshAE48rZlKVqrhp5CYtgsH37yw3riEtSwY7NVxjqP_AwbmrecSmBXzDxI1LxnUTF6VICfgt7Jy2VYUmsorxFQ0HERbCu8yXUFgLyaY84gOKm8WowBWrUtFpIFokOwLOsb3B7Y4ElPjY14Qk--Z8hfpGB0mdmXtuXNyo39U_sFo.DXbsPcNz580OtEQ3onWLsyyqpTrn6IH46JBlLz_D71g&dib_tag=se&keywords=gaming+keyboard&pd_rd_r=9cd89933-ec18-4062-9291-19ef9131fcd0&pd_rd_w=VcDAo&pd_rd_wg=tLLQL&pf_rd_p=12129333-2117-4490-9c17-6d31baf0582a&pf_rd_r=NG0EY08GTNTBY7RQE9MD&qid=1708243088&sr=8-2"
url3 <- "https://www.amazon.com/Mechanical-Keyboard-MageGee-Backlit-Computer/dp/B09M9HB4PV/ref=sr_1_3?_encoding=UTF8&content-id=amzn1.sym.12129333-2117-4490-9c17-6d31baf0582a&dib=eyJ2IjoiMSJ9.xPISJOYMxoc_9dHbx858fyuH96vplirkkEV9nhvcubZg0TSfKqKKtaNlrROmqgkkAshAE48rZlKVqrhp5CYtgsH37yw3riEtSwY7NVxjqP_AwbmrecSmBXzDxI1LxnUTF6VICfgt7Jy2VYUmsorxFQ0HERbCu8yXUFgLyaY84gOKm8WowBWrUtFpIFokOwLOsb3B7Y4ElPjY14Qk--Z8hfpGB0mdmXtuXNyo39U_sFo.DXbsPcNz580OtEQ3onWLsyyqpTrn6IH46JBlLz_D71g&dib_tag=se&keywords=gaming+keyboard&pd_rd_r=9cd89933-ec18-4062-9291-19ef9131fcd0&pd_rd_w=VcDAo&pd_rd_wg=tLLQL&pf_rd_p=12129333-2117-4490-9c17-6d31baf0582a&pf_rd_r=NG0EY08GTNTBY7RQE9MD&qid=1708243172&sr=8-3"
url4 <- "https://www.amazon.com/Razer-Ornata-Gaming-Keyboard-Low-Profile/dp/B09X6GJ691/ref=sr_1_4?_encoding=UTF8&content-id=amzn1.sym.12129333-2117-4490-9c17-6d31baf0582a&dib=eyJ2IjoiMSJ9.xPISJOYMxoc_9dHbx858fyuH96vplirkkEV9nhvcubZg0TSfKqKKtaNlrROmqgkkAshAE48rZlKVqrhp5CYtgsH37yw3riEtSwY7NVxjqP_AwbmrecSmBXzDxI1LxnUTF6VICfgt7Jy2VYUmsorxFQ0HERbCu8yXUFgLyaY84gOKm8WowBWrUtFpIFokOwLOsb3B7Y4ElPjY14Qk--Z8hfpGB0mdmXtuXNyo39U_sFo.DXbsPcNz580OtEQ3onWLsyyqpTrn6IH46JBlLz_D71g&dib_tag=se&keywords=gaming+keyboard&pd_rd_r=9cd89933-ec18-4062-9291-19ef9131fcd0&pd_rd_w=VcDAo&pd_rd_wg=tLLQL&pf_rd_p=12129333-2117-4490-9c17-6d31baf0582a&pf_rd_r=NG0EY08GTNTBY7RQE9MD&qid=1708243172&sr=8-4"
url5 <- "https://www.amazon.com/Womier-Percent-Keyboard-Mechanical-Hot-Swappable/dp/B0BVVYW6L6/ref=sr_1_5?_encoding=UTF8&content-id=amzn1.sym.12129333-2117-4490-9c17-6d31baf0582a&dib=eyJ2IjoiMSJ9.xPISJOYMxoc_9dHbx858fyuH96vplirkkEV9nhvcubZg0TSfKqKKtaNlrROmqgkkAshAE48rZlKVqrhp5CYtgsH37yw3riEtSwY7NVxjqP_AwbmrecSmBXzDxI1LxnUTF6VICfgt7Jy2VYUmsorxFQ0HERbCu8yXUFgLyaY84gOKm8WowBWrUtFpIFokOwLOsb3B7Y4ElPjY14Qk--Z8hfpGB0mdmXtuXNyo39U_sFo.DXbsPcNz580OtEQ3onWLsyyqpTrn6IH46JBlLz_D71g&dib_tag=se&keywords=gaming+keyboard&pd_rd_r=9cd89933-ec18-4062-9291-19ef9131fcd0&pd_rd_w=VcDAo&pd_rd_wg=tLLQL&pf_rd_p=12129333-2117-4490-9c17-6d31baf0582a&pf_rd_r=NG0EY08GTNTBY7RQE9MD&qid=1708243172&sr=8-5" 

session1 <- bow(url1, user_agent = "Educational Purposes")
session2 <- bow(url2, user_agent = "EDucational Purposes")
session3 <- bow(url3, user_agent = "EDUcational Purposes")
session4 <- bow(url4, user_agent = "EDUCational Purposes")
session5 <- bow(url5, user_agent = "EDUCAtional Purposes")

session1
session2
session3
session4
session5
```
Url
```{r}
keyboard_url1 <- read_html(url1)
keyboard_url2 <- read_html(url2)
keyboard_url3 <- read_html(url3)
keyboard_url4 <- read_html(url4)
keyboard_url5 <- read_html(url5)
```
Scrape for the Name of the Product
```{r}
keyboardName1 <- keyboard_url1 %>%
  html_nodes("") %>%
  html_text
keyboardName1
```


```{r}
keyboardName2 <- keyboard_url2 %>%
  html_nodes("") %>%
  html_text
keyboardName2

keyboardName3 <- keyboard_url3 %>%
  html_nodes("") %>%
  html_text
keyboardName3

keyboardName4 <- keyboard_url4 %>%
  html_nodes("") %>%
  html_text
keyboardName4

keyboardName5 <- keyboard_url5 %>%
  html_nodes("") %>%
  html_text
keyboardName5
```
Merge it into Data Frame 
```{r}
keyboarddf1 <- data.frame(keyboardName1)
keyboarddf2 <- data.frame(keyboardName2)
keyboarddf3 <- data.frame(keyboardName3)
keyboarddf4 <- data.frame(keyboardName4)
keyboarddf5 <- data.frame(keyboardName5)

keyboarddf <- cbind(keyboarddf1,keyboarddf2,keyboarddf3,keyboarddf4,keyboarddf5)
keyboarddf
```
Scrape the Price for the first 22 products
```{r}
keyboardPrice <- keyboard_url1 %>%
  html_nodes("span.a-price.aok-align-center.reinventPricePriceToPayMargin.priceToPay") %>%
  html_text()

First_Price <- str_extract(keyboardPrice[1:22], "\\$[0-9.]+")
First_Price

keyboardPrice1 <- data.frame(First_Price)

keyboardProduct1 <- cbind(keyboarddf1, keyboardPrice1)
keyboardProduct1

#Change the Column Names

newcolumn <- c("ProductName", "ProductPrice")
colnames(keyboardProduct1) = newcolumn

mouseProduct1
```
Scrape the Ratings
```{r}
keyboardRatings <- mouseURL %>%
  html_nodes("i.a-icon.a-icon-star-small.a-star-small-4-5.aok-align-bottom") %>%
  html_text()
keyboardRatings

sukeyboardRatings <- keyboardRatings[1:22]

keyboardProduct1 <- cbind()

```
Scrape the Total No. of Reviews
```{r}
keyboardTotalRev1 <- keyboard_url1 %>%
  html_nodes("span#acrCustomerReviewText.a-size-base") %>%
  html_text()
keyboardTotalRev1
```
Merge it in Data Frame
```{r}
data_frame1 <- data.frame(
  Product_Name = keyboardName1,
  Price = keyboadPrice1,
  Ratings = keyboardRatings1,
  Reviews = keyboardTotalRev1
)
data_frame1
```
```{r}

  library(rvest)
  library(polite)
  library(httr)
  library(dplyr)

url2 <- "https://www.amazon.com/Redragon-S101-Keyboard-Ergonomic-Programmable/dp/B00NLZUM36/ref=sr_1_2?_encoding=UTF8&content-id=amzn1.sym.12129333-2117-4490-9c17-6d31baf0582a&dib=eyJ2IjoiMSJ9.xPISJOYMxoc_9dHbx858f_O35VE9n8_s6WvG1ovb3cKq_CSeRgiViZDzlpzYoM86AshAE48rZlKVqrhp5CYtgi63zqI2DyCKo__fF7Vik3PLLeCQlB8QU-fCKFSY07sQLAFPVLMiQZy1rIK-42IJheLHnntBCGG05tb7MbAiQ_VT__toOsEk9FcXRswjbJpryZw3FragLIqgJTdcl4UAkRx5gcMEensmGLkqfNQBH-g.Ewv4sqhL3VCmDHjkktWJnYiJ-gfyD2ndRwLOHc0YMaM&dib_tag=se&keywords=gaming+keyboard&pd_rd_r=3891b178-b803-44e5-af31-5ce03e34ab3a&pd_rd_w=Pq9TS&pd_rd_wg=2JYj1&pf_rd_p=12129333-2117-4490-9c17-6d31baf0582a&pf_rd_r=F4AJRN21H9B3MK2W6ZY1&qid=1707956797&sr=8-2"


keyboard_url2 <- read_html(url2)
```
Scrape for the Name of the Product
```{r}
keyboardName2 <- keyboard_url2 %>%
  html_nodes("h1#title.a-size-large.a-spacing-none") %>%
  html_text
keyboardName1
```
Scrape the Price
```{r}
keyboardPrice2 <- keyboard_url2 %>%
  html_nodes("span.a-price.aok-align-center.reinventPricePriceToPayMargin.priceToPay") %>%
  html_text()
keyboardPrice2
```
Scrape the Ratings
```{r}
keyboardRatings2 <- keyboard_url2 %>%
  html_nodes("i.a-icon.a-icon-star.a-star-4-5.cm-cr-review-stars-spacing-big") %>%
  html_text()
keyboardRatings2
```
Scrape the Total No. of Reviews
```{r}
keyboardTotalRev2 <- keyboard_url2 %>%
  html_nodes("span#acrCustomerReviewText.a-size-base") %>%
  html_text()
keyboardTotalRev2
```

```{r}

  library(rvest)
  library(polite)
  library(httr)
  library(dplyr)

url3 <- "https://www.amazon.com/Redragon-S101-Keyboard-Ergonomic-Programmable/dp/B00NLZUM36/ref=sr_1_2?_encoding=UTF8&content-id=amzn1.sym.12129333-2117-4490-9c17-6d31baf0582a&dib=eyJ2IjoiMSJ9.xPISJOYMxoc_9dHbx858f_O35VE9n8_s6WvG1ovb3cKq_CSeRgiViZDzlpzYoM86AshAE48rZlKVqrhp5CYtgi63zqI2DyCKo__fF7Vik3PLLeCQlB8QU-fCKFSY07sQLAFPVLMiQZy1rIK-42IJheLHnntBCGG05tb7MbAiQ_VT__toOsEk9FcXRswjbJpryZw3FragLIqgJTdcl4UAkRx5gcMEensmGLkqfNQBH-g.Ewv4sqhL3VCmDHjkktWJnYiJ-gfyD2ndRwLOHc0YMaM&dib_tag=se&keywords=gaming+keyboard&pd_rd_r=3891b178-b803-44e5-af31-5ce03e34ab3a&pd_rd_w=Pq9TS&pd_rd_wg=2JYj1&pf_rd_p=12129333-2117-4490-9c17-6d31baf0582a&pf_rd_r=F4AJRN21H9B3MK2W6ZY1&qid=1707956797&sr=8-2"
keyboard_url3 <- read_html(url3)
```

Scrape for the Name of the Product
```{r}

```
Scrape the Price
```{r}
keyboardPrice3 <- keyboard_url3 %>%
  html_nodes("span.a-price.aok-align-center.reinventPricePriceToPayMargin.priceToPay") %>%
  html_text()
keyboardPrice3
```
Scrape the Ratings
```{r}
keyboardRatings3 <- keyboard_url3 %>%
  html_nodes("i.a-icon.a-icon-star.a-star-4-5.cm-cr-review-stars-spacing-big") %>%
  html_text()
keyboardRatings3
```
Scrape the Total No. of Reviews
```{r}
keyboardTotalRev3 <- keyboard_url3 %>%
  html_nodes("span#acrCustomerReviewText.a-size-base") %>%
  html_text()
keyboardTotalRev3
```

```{r}
url4 <- "https://www.amazon.com/Redragon-S101-Keyboard-Ergonomic-Programmable/dp/B00NLZUM36/ref=sr_1_2?_encoding=UTF8&content-id=amzn1.sym.12129333-2117-4490-9c17-6d31baf0582a&dib=eyJ2IjoiMSJ9.xPISJOYMxoc_9dHbx858f_O35VE9n8_s6WvG1ovb3cKq_CSeRgiViZDzlpzYoM86AshAE48rZlKVqrhp5CYtgi63zqI2DyCKo__fF7Vik3PLLeCQlB8QU-fCKFSY07sQLAFPVLMiQZy1rIK-42IJheLHnntBCGG05tb7MbAiQ_VT__toOsEk9FcXRswjbJpryZw3FragLIqgJTdcl4UAkRx5gcMEensmGLkqfNQBH-g.Ewv4sqhL3VCmDHjkktWJnYiJ-gfyD2ndRwLOHc0YMaM&dib_tag=se&keywords=gaming+keyboard&pd_rd_r=3891b178-b803-44e5-af31-5ce03e34ab3a&pd_rd_w=Pq9TS&pd_rd_wg=2JYj1&pf_rd_p=12129333-2117-4490-9c17-6d31baf0582a&pf_rd_r=F4AJRN21H9B3MK2W6ZY1&qid=1707956797&sr=8-2"
keyboard_url4 <- read_html(url4)
```

Scrape for the Name of the Product
```{r}

```
Scrape the Price
```{r}
keyboardPrice4 <- keyboard_url4 %>%
  html_nodes("span.a-price.aok-align-center.reinventPricePriceToPayMargin.priceToPay") %>%
  html_text()
keyboardPrice4
```
Scrape the Ratings
```{r}
keyboardRatings4 <- keyboard_url4 %>%
  html_nodes("i.a-icon.a-icon-star.a-star-4-5.cm-cr-review-stars-spacing-big") %>%
  html_text()
keyboardRatings4
```
Scrape the Total No. of Reviews
```{r}
keyboardTotalRev4 <- keyboard_url4 %>%
  html_nodes("span#acrCustomerReviewText.a-size-base") %>%
  html_text()
keyboardTotalRev4
```

```{r}
url5 <- "https://www.amazon.com/Redragon-S101-Keyboard-Ergonomic-Programmable/dp/B00NLZUM36/ref=sr_1_2?_encoding=UTF8&content-id=amzn1.sym.12129333-2117-4490-9c17-6d31baf0582a&dib=eyJ2IjoiMSJ9.xPISJOYMxoc_9dHbx858f_O35VE9n8_s6WvG1ovb3cKq_CSeRgiViZDzlpzYoM86AshAE48rZlKVqrhp5CYtgi63zqI2DyCKo__fF7Vik3PLLeCQlB8QU-fCKFSY07sQLAFPVLMiQZy1rIK-42IJheLHnntBCGG05tb7MbAiQ_VT__toOsEk9FcXRswjbJpryZw3FragLIqgJTdcl4UAkRx5gcMEensmGLkqfNQBH-g.Ewv4sqhL3VCmDHjkktWJnYiJ-gfyD2ndRwLOHc0YMaM&dib_tag=se&keywords=gaming+keyboard&pd_rd_r=3891b178-b803-44e5-af31-5ce03e34ab3a&pd_rd_w=Pq9TS&pd_rd_wg=2JYj1&pf_rd_p=12129333-2117-4490-9c17-6d31baf0582a&pf_rd_r=F4AJRN21H9B3MK2W6ZY1&qid=1707956797&sr=8-2"
keyboard_url5 <- read_html(url5)
```
Scrape for the Name of the Product
```{r}

```
Scrape the Price
```{r}
keyboardPrice5 <- keyboard_url5 %>%
  html_nodes("span.a-price.aok-align-center.reinventPricePriceToPayMargin.priceToPay") %>%
  html_text()
keyboardPrice5
```
Scrape the Ratings
```{r}
keyboardRatings5 <- keyboard_url5 %>%
  html_nodes("i.a-icon.a-icon-star.a-star-4-5.cm-cr-review-stars-spacing-big") %>%
  html_text()
keyboardRatings5
```
Scrape the Total No. of Reviews
```{r}
keyboardTotalRev5 <- keyboard_url5 %>%
  html_nodes("span#acrCustomerReviewText.a-size-base") %>%
  html_text()
keyboardTotalRev5
```