---
title: "Lab_Exercise_1"
author: "Natalie Joy Loredo"
date: "2024-02-24"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Web Scraping
200 PRODUCTS
```{r}
#Web Scraping200 PRODUCTS
library(rvest)
library(dplyr)
library(polite)
library(stringr) 
library(httr)

url <- "https://www.amazon.co.uk/b/?node=13978262031&ref_=Oct_d_odnav_300703&pd_rd_w=cmdmk&content-id=amzn1.sym.c6fcbfa3-a0cb-49d1-be17-9aeb9a6d61f8&pf_rd_p=c6fcbfa3-a0cb-49d1-be17-9aeb9a6d61f8&pf_rd_r=J8QWJKKB1ZEDHB1NJXBQ&pd_rd_wg=gk7DE&pd_rd_r=9fef13c7-e7f2-4617-b4ec-62edfbc2d9ca"

session <- bow(url, user_agent = "Educational Purposes")
session


session_1 <- session ("https://www.amazon.co.uk/b/?node=13978262031&ref_=Oct_d_odnav_300703&pd_rd_w=cmdmk&content-id=amzn1.sym.c6fcbfa3-a0cb-49d1-be17-9aeb9a6d61f8&pf_rd_p=c6fcbfa3-a0cb-49d1-be17-9aeb9a6d61f8&pf_rd_r=J8QWJKKB1ZEDHB1NJXBQ&pd_rd_wg=gk7DE&pd_rd_r=9fef13c7-e7f2-4617-b4ec-62edfbc2d9ca")

#Name
name1 <- session_1 %>%
  html_nodes("h2") %>%
  html_text()

names<- name1[1:50]
names

#Price
price1 <- session_1 %>%
  html_nodes("span.a-price") %>%
  html_text()

prices1<- price1[1:50]
prices1

#Rating
ratings1 <- session_1 %>%
  html_nodes("span.a-size-base.s-underline-text") %>%
  html_text()

rate<- ratings1[1:50]
rate

#Review
reviews1 <- session_1 %>%
  html_nodes("span.a-icon-alt") %>%
  html_text()

rev<- reviews1[1:50]
rev

framedf1 <- data.frame(
  Name = names, 
  Price =prices1, 
  Ratings = rate, 
  Reviews = rev
)
framedf1
```

```{r}
write.csv(framedf1, "Products1.csv")
read.csv("Products1.csv")
```

```{r}
url2 <- "https://www.amazon.co.uk/b/?node=13978690031&ref_=Oct_d_odnav_300703&pd_rd_w=cmdmk&content-id=amzn1.sym.c6fcbfa3-a0cb-49d1-be17-9aeb9a6d61f8&pf_rd_p=c6fcbfa3-a0cb-49d1-be17-9aeb9a6d61f8&pf_rd_r=J8QWJKKB1ZEDHB1NJXBQ&pd_rd_wg=gk7DE&pd_rd_r=9fef13c7-e7f2-4617-b4ec-62edfbc2d9ca"

session_2 <- bow(url2, user_agent = "Educational Purposes")
session_2


session_2 <- session("https://www.amazon.co.uk/b/?node=13978690031&ref_=Oct_d_odnav_300703&pd_rd_w=cmdmk&content-id=amzn1.sym.c6fcbfa3-a0cb-49d1-be17-9aeb9a6d61f8&pf_rd_p=c6fcbfa3-a0cb-49d1-be17-9aeb9a6d61f8&pf_rd_r=J8QWJKKB1ZEDHB1NJXBQ&pd_rd_wg=gk7DE&pd_rd_r=9fef13c7-e7f2-4617-b4ec-62edfbc2d9ca") 


#Name
name2 <- session_2 %>%
  html_nodes("h2") %>%
  html_text()

names2<- name2[1:50]
names2

#Price 
price2 <- session_2 %>%
  html_nodes("span.a-price") %>%
  html_text()

prices2<- price2[1:50]
prices2

#Ratings
ratings2 <- session_2 %>%
  html_nodes("span.a-size-base.s-underline-text") %>%
  html_text()

rate2<- ratings2[1:50]
rate2

#Reviews
reviews2 <- session_2 %>%
  html_nodes("span.a-icon-alt") %>%
  html_text()

rev2<- reviews2[1:50]
rev2

framedf2 <- data.frame(
  Name = names2, 
  Price = prices2, 
  Ratings = rate2, 
  Reviews = rev2
)
framedf2
```

```{r}
write.csv(framedf2, "Products2.csv")
read.csv("Products2.csv")
```

```{r}
url3 <- "https://www.amazon.co.uk/s?rh=n%3A13978266031&language=en_GB&brr=1&content-id=amzn1.sym.c6fcbfa3-a0cb-49d1-be17-9aeb9a6d61f8&pd_rd_r=d9cda3d1-5bc6-457e-9c38-f2c38865fc78&pd_rd_w=p5fp2&pd_rd_wg=6Icg2&pf_rd_p=c6fcbfa3-a0cb-49d1-be17-9aeb9a6d61f8&pf_rd_r=79J2F5CZ11K78247Y4M8&rd=1&ref=Oct_d_odnav_300703"


session_3 <- bow(url3, user_agent = "Educational Purposes")
session_3


library(rvest)
library(stringr)
library(httr2)
library(httr) 

session_3 <- session("https://www.amazon.co.uk/s?rh=n%3A13978266031&language=en_GB&brr=1&content-id=amzn1.sym.c6fcbfa3-a0cb-49d1-be17-9aeb9a6d61f8&pd_rd_r=d9cda3d1-5bc6-457e-9c38-f2c38865fc78&pd_rd_w=p5fp2&pd_rd_wg=6Icg2&pf_rd_p=c6fcbfa3-a0cb-49d1-be17-9aeb9a6d61f8&pf_rd_r=79J2F5CZ11K78247Y4M8&rd=1&ref=Oct_d_odnav_300703")

#Name
name3 <- session_3 %>%
  html_nodes("h2") %>%
  html_text()

names3<- name3[1:24]
names3

#Price 
price3 <- session_3 %>%
  html_nodes("span.a-price") %>%
  html_text()

prices3<- price3[1:24]
prices3

#Rating
ratings3 <- session_3 %>%
  html_nodes("span.a-size-base.s-underline-text") %>%
  html_text()

rate3<- ratings3[1:24]
rate3

#Reviews
reviews3 <- session_3 %>%
  html_nodes("span.a-icon-alt") %>%
  html_text()

rev3<- reviews3[1:24]
rev3

framedf3 <- data.frame(
  Name = names3, 
  Price = prices3, 
  Rating = rate3, 
  Reviews = rev3
)
framedf3
```

```{r}
write.csv(framedf3, "Products3.csv")
read.csv("Products3.csv")
```


```{r}
url4 <- "https://www.amazon.co.uk/s?i=videogames&rh=n%3A13978266031&page=2&language=en_GB&brr=1&content-id=amzn1.sym.c6fcbfa3-a0cb-49d1-be17-9aeb9a6d61f8&pd_rd_r=d9cda3d1-5bc6-457e-9c38-f2c38865fc78&pd_rd_w=p5fp2&pd_rd_wg=6Icg2&pf_rd_p=c6fcbfa3-a0cb-49d1-be17-9aeb9a6d61f8&pf_rd_r=79J2F5CZ11K78247Y4M8&qid=1709966906&rd=1&ref=sr_pg_2"

session4 <- bow(url4, user_agent = "Educational Purposes")
session4

session_4 <- scrape(session4)
session_4

#Name
name4 <- session_4 %>%
  html_nodes("h2") %>%
  html_text()

names4<- name4[1:24]
names

#Price
price4 <- session_4 %>%
  html_nodes("span.a-price") %>%
  html_text()

prices4<- price4[1:24]
prices4

#Ratings
ratings4<- session_4 %>%
  html_nodes("span.a-size-base.s-underline-text") %>%
  html_text()

rate4<- ratings4[1:24]
rate4

#Reviews
reviews4 <- session_4 %>%
  html_nodes("span.a-icon-alt") %>%
  html_text()

rev4<- reviews4[1:24]
rev4

framedf4 <- data.frame(
  Name = names4, 
  Price = prices4, 
  Rating = rate4, 
  Reviews = rev4
)
framedf4
```

```{r}
write.csv(framedf4, "Products4.csv")
read.csv("Products4.csv")
```

```{r}
url5 <- "https://www.amazon.co.uk/s?i=videogames&rh=n%3A13978266031&page=3&language=en_GB&brr=1&content-id=amzn1.sym.c6fcbfa3-a0cb-49d1-be17-9aeb9a6d61f8&pd_rd_r=d9cda3d1-5bc6-457e-9c38-f2c38865fc78&pd_rd_w=p5fp2&pd_rd_wg=6Icg2&pf_rd_p=c6fcbfa3-a0cb-49d1-be17-9aeb9a6d61f8&pf_rd_r=79J2F5CZ11K78247Y4M8&qid=1709967016&rd=1&ref=sr_pg_3" 

session5 <- bow(url5, user_agent = "Educational Purposes")
session5

session_5 <- scrape(session5)
session_5

#Name
name5 <- session_5 %>%
  html_nodes("h2") %>%
  html_text()

names5<- name5[1:24]
names5

#Price
price5 <- session_5 %>%
  html_nodes("span.a-price") %>%
  html_text()

prices5<- price5[1:24]
prices5

#Ratings
ratings5 <- session_5 %>%
  html_nodes("span.a-size-base.s-underline-text") %>%
  html_text()

rate5<- ratings5[1:24]
rate5

#Reviews 
reviews5<- session_5 %>%
  html_nodes("span.a-icon-alt") %>%
  html_text()

rev5<- reviews5[1:24]
rev5

framedf5 <- data.frame(
  Name = names5, 
  Price = prices5, 
  Rating = rate5, 
  Reviews = rev5
)
framedf5
```

```{r}
write.csv(framedf5, "Products5.csv")
read.csv("Products5.csv")
```

```{r}
url6 <- "https://www.amazon.co.uk/s?i=videogames&rh=n%3A13978266031&page=4&language=en_GB&brr=1&content-id=amzn1.sym.c6fcbfa3-a0cb-49d1-be17-9aeb9a6d61f8&pd_rd_r=d9cda3d1-5bc6-457e-9c38-f2c38865fc78&pd_rd_w=p5fp2&pd_rd_wg=6Icg2&pf_rd_p=c6fcbfa3-a0cb-49d1-be17-9aeb9a6d61f8&pf_rd_r=79J2F5CZ11K78247Y4M8&qid=1709967029&rd=1&ref=sr_pg_4"

session6 <- bow(url6, user_agent = "Educational Purposes")
session6

session_6 <- scrape(session6)
session_6

#Names
name6<- session_6 %>%
  html_nodes("h2") %>%
  html_text()

names6<- name6[1:30]
names6

#Price
price6 <- session_6 %>%
  html_nodes("span.a-price") %>%
  html_text()

prices6<- price6[1:30]
prices6

#Ratings
ratings6 <- session_6 %>%
  html_nodes("span.a-size-base.s-underline-text") %>%
  html_text()

rate6<- ratings6[1:30]
rate6

#Review
reviews6 <- session_6 %>%
  html_nodes("span.a-icon-alt") %>%
  html_text()

rev6<- reviews6[1:30]
rev6

framedf6 <- data.frame(
  Name = names6, 
  Price = prices6, 
  Rating = rate6, 
  Reviews = rev6
)
framedf6
```

```{r}
write.csv(framedf6, "Products6.csv")
read.csv("Products6.csv")
```
CSV for 200 products
```{r}
productsdf <- bind_rows( framedf3, 
                  	framedf2,
                   	framedf3, 
                   	framedf4, 
                   	framedf6, 
                  	framedf6)
productsdf
```

```{r}
write.csv(productsdf, "200ProductsReviews.csv")
read.csv("200ProductsReviews.csv")
```
Get the 25 Reviews
```{r}
#1st Product
library(rvest)

url1 <- "https://www.amazon.com.au/product-reviews/B0BHSS55RM/ref=acr_search_hist_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews#reviews-filter-bar"

session1 <-bow(url1, user_agent = "Educational Purposes")
sessionn1<- scrape(session1)

#Name of the reviewer
namereview1 <- sessionn1 %>%
  html_nodes("span.a-profile-name") %>%
  html_text()

names_1<- namereview1[1:25] 
names_1

#Date of review
date1 <- sessionn1 %>%
  html_nodes("span.review-date") %>%
  html_text()

datereview<- date1[1:25]
datereview

#Individual  rating
rates1 <- sessionn1 %>%
  html_nodes("span.a-icon-alt") %>%
  html_text()

indivrate <- rates1[1:25]

# Review comment
comrev1 <- sessionn1 %>%
  html_nodes("span.a-size-base.review-text.review-text-content") %>%
  html_text()

reviews_com <- comrev1[1:25]
reviews_com <- gsub("\n", "", reviews_com)

framedf1 <- data.frame(
  Name = names_1, 
  Date = datereview, 
  Individual_Rating = indivrate, 
  Review = reviews_com
)
framedf1

write.csv(framedf1, "ProductsReviews1.csv")
read.csv("ProductsReviews1.csv")
```
SECOND
```{r}
#2ndProduct

library(rvest)

url_2 <- "https://www.amazon.com.au/product-reviews/B0BTG4S29L/ref=acr_dpx_hist_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews#reviews-filter-bar"

session2<-bow(url_2, user_agent = "Educational Purposes")
sessionn2 <- scrape(session2)

#Name of the reviewer
namereview2 <- sessionn2 %>%
  html_nodes("span.a-profile-name") %>%
  html_text()

names_2<- namereview2[1:25] 
names_2

#Date of review
date2 <- sessionn1 %>%
  html_nodes("span.review-date") %>%
  html_text()

datereview2<- date2[1:25]
datereview2

#Individual  rating
rates2 <- sessionn2 %>%
  html_nodes("span.a-icon-alt") %>%
  html_text()

indivrate2 <- rates2[1:25]
indivrate2

#Review comment
comrev2 <- sessionn2 %>%
  html_nodes("span.a-size-base.review-text.review-text-content") %>%
  html_text()

reviews_com2 <- comrev2[1:25]
reviews_com2 <- gsub("\n", "", reviews_com2)

framedf2 <- data.frame(
  Name = names_2, 
  Date = datereview2, 
  Individual_Rating = indivrate2, 
  Review = reviews_com2
)
framedf2

write.csv(framedf2, "ProductsReviews2.csv")
read.csv("ProductsReviews2.csv")
```
THIRD
```{r}
#3rdProduct

url_3 <- "https://www.amazon.com.au/product-reviews/B086WCG4SR/ref=p13n_ds_purchase_sim_1p_dp_desktop_d_sccl_1_2_cr/358-8254970-8794523?pd_rd_w=1SxUI&content-id=amzn1.sym.26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_p=26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_r=VX1KZQGA39ET6N51N4EP&pd_rd_wg=gaSN9&pd_rd_r=e92d4990-3f8e-486c-aebc-96f58ad50280&pd_rd_i=B086WCG4SR"

session3 <-bow(url_3, user_agent = "Educational Purposes")
sessionn3 <- scrape(session3)
sessionn3

product3 <- "https://www.amazon.com.au/product-reviews/B086WCG4SR/ref=cm_cr_arp_d_viewopt_srt/358-8254970-8794523?pd_rd_w=1SxUI&content-id=amzn1.sym.26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_p=26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_r=VX1KZQGA39ET6N51N4EP&pd_rd_wg=gaSN9&pd_rd_r=e92d4990-3f8e-486c-aebc-96f58ad50280&pd_rd_i=B086WCG4SR&pageNumber=1&sortBy=recent"

sessionn_3 <-bow(product3, user_agent = "Educational Purposes")
sessionnn3 <- scrape(sessionn_3)
sessionnn3

#Name of the reviewer
namereview3 <- sessionn3 %>%
  html_nodes("span.a-profile-name") %>%
  html_text()

names_3<- namereview3[1:15] 
names_3

#Date of review
date3 <- sessionn3 %>%
  html_nodes("span.review-date") %>%
  html_text()

datereview3<- date3[1:15]
datereview3

#Individual rating
rates3 <- sessionn3 %>%
  html_nodes("span.a-icon-alt") %>%
  html_text()

indivrate3<- rates3[1:15]
indivrate3

#Review comment 
comrev3 <- sessionn3 %>%
  html_nodes("span.a-size-base.review-text.review-text-content") %>%
  html_text()

reviews_com3 <- comrev3[1:15]
reviews_com3 <- gsub("\n", "", reviews_com3)

framedf3 <- data.frame(
  Name = names_3, 
  Date = datereview3, 
  Individual_Rating = indivrate3, 
  Review = reviews_com3
)
framedf3

#Name of reviewer
namereview_3 <- sessionnn3 %>%
  html_nodes("span.a-profile-name") %>%
  html_text()

names_3 <- namereview_3 [1:10]
names_3

#Date of review
date_3 <- sessionnn3 %>%
  html_nodes("span.review-date") %>%
  html_text()

datereview_3<- date_3[1:10]
datereview_3

#Individual rating
rates_3 <- sessionnn3 %>%
  html_nodes("span.a-icon-alt") %>%
  html_text()

indivrate_3 <- rates_3 [1:10]
indivrate_3

#Review comment 
comrev_3 <- sessionnn3 %>%
  html_nodes("span.a-size-base.review-text.review-text-content") %>%
  html_text()

reviewscom_3 <- comrev_3[1:10]
reviewscom_3 <- gsub("\n", "", reviewscom_3)


framedf_3 <- data.frame(
  Name = names_3, 
  Date = datereview_3, 
  Individual_Rating = indivrate_3, 
  Review = reviewscom_3
)
framedf_3

framedff3 <- bind_rows(framedf3,framedf_3)
framedff3

write.csv(framedff3, "ProductsReviews3.csv")
read.csv("ProductsReviews3.csv")
```

FOURTH
```{r}

#4th product
library(rvest)
library(dplyr)
library(httr2)
library(httr)
library(purrr)


url_4 <- "https://www.amazon.com.au/product-reviews/B09TDTJKF1/ref=cm_cr_arp_d_viewopt_srt?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&sortBy=recent&pageNumber=1#reviews-filter-bar"

session4 <- bow(url_4, user_agent = "Educational Purposes")
sessionn4 <- scrape(session4)
sessionn4

product4 <-"https://www.amazon.com.au/product-reviews/B09TDTJKF1/ref=cm_cr_getr_d_paging_btm_next_2?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&sortBy=recent&pageNumber=2#reviews-filter-bar"

session_4<- bow(product4, user_agent = "Educational Purposes")
sessionnn4 <- scrape(session_4)
sessionnn4

#Name of reviewer
namereview4 <- sessionn4 %>%
  html_nodes("span.a-profile-name") %>%
  html_text()

namee4 <- namereview4 [1:12]
namee4

#Date of review
date4 <- sessionn4 %>%
  html_nodes("span.review-date") %>%
  html_text()

datereview4 <- date4[1:12]
datereview4

#Individual rating
rates4 <- sessionn4 %>%
  html_nodes("span.a-icon-alt") %>%
  html_text()

indivrate4 <- rates4[1:12]
indivrate4

#Review comment 
comrev4 <- sessionn4 %>%
  html_nodes("span.a-size-base.review-text.review-text-content") %>%
  html_text()

reviewscom4 <- comrev4[1:12]
reviewscom4 <- gsub("\n", "", reviewscom4)

framedf4 <- data.frame(
  Name = namee4, 
  Date = datereview4, 
  Individual_Rating = indivrate4, 
  Review = reviewscom4
)
framedf4

#Name of reviewer
namereview_4<- sessionn4 %>%
  html_nodes("span.a-profile-name") %>%
  html_text()

namee_4 <- namereview_4 [1:13]
namee_4

#Date of review
date_4 <- sessionnn4 %>%
  html_nodes("span.review-date") %>%
  html_text()

datereview_4 <- date_4[1:13]
datereview_4

#Individual rating
rates_4 <- sessionnn4 %>%
  html_nodes("span.a-icon-alt") %>%
  html_text()

indivrate_4 <- rates_4[1:13]
indivrate_4

#Review comment 
comrev_4 <- sessionnn4 %>%
  html_nodes("span.a-size-base.review-text.review-text-content") %>%
  html_text()

reviewscom_4 <- comrev_4 [1:13]
reviewscom_4<- gsub("\n", "", reviewscom_4)

framedf_4 <- data.frame(
  Name = namee_4, 
  Date = datereview_4, 
  Individual_Rating = indivrate_4, 
  Review = reviewscom_4
)
framedf_4

frame_df4 <- bind_rows(framedf4,framedf_4)
frame_df4

write.csv(frame_df4, "ProductsReviews4.csv")
read.csv("ProductsReviews4.csv")
```
FIFTH
```{r}
#5th product 

url_5 <- "https://www.amazon.com/product-reviews/B0C7GYX6MH/ref=acr_search_hist_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews#reviews-filter-bar"

session5 <- bow(url_5, user_agent = "Educational Purposes")
sessionn5 <- scrape(session5)
sessionn5

product5 <- "https://www.amazon.com/product-reviews/B0C7GYX6MH/ref=acr_search_hist_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews#reviews-filter-bar"

session_5 <- bow(product5, user_agent = "Educational Purposes")
sessionnn5 <- scrape(session_5)
sessionnn5

library(rvest)
library(stringr)
library(httr2)
library(httr) 

#Name of reviewer
namereview5 <- sessionn5 %>%
  html_nodes("span.a-profile-name") %>%
  html_text()

namee5 <- namereview5 [1:13]
namee5

#Date of review
date5<- sessionn5 %>%
  html_nodes("span.review-date") %>%
  html_text()

datereview5 <- date5[1:13]
datereview5

#Individual rating
rates5 <- sessionn5 %>%
  html_nodes("span.a-icon-alt") %>%
  html_text()

indivrate5 <- rates5[1:13]
indivrate5

#Review comment 
comrev5 <- sessionn5 %>%
  html_nodes("span.a-size-base.review-text.review-text-content") %>%
  html_text()

reviewscom5 <- comrev5[1:13]
reviewscom5 <- gsub("\n", "", reviewscom5)
reviewscom5

framedf5 <- data.frame(
  Name = namee5, 
  Date = datereview5, 
  Individual_Rating = indivrate5, 
  Review = reviewscom5 
)
framedf5

#Name of reviewer
namereview_5 <- sessionnn5 %>%
  html_nodes("span.a-profile-name") %>%
  html_text()

namee_5 <- namereview_5[1:13]
namee_5

#Date of review
date_5<- sessionnn5 %>%
  html_nodes("span.review-date") %>%
  html_text()

datereview_5 <- date_5[1:13]
datereview_5

#Individual rating
rates_5 <- sessionnn5 %>%
  html_nodes("span.a-icon-alt") %>%
  html_text()

indivrate_5 <- rates_5[1:13]
indivrate_5

#Review comment 
comrev_5 <- sessionnn5 %>%
  html_nodes("span.a-size-base.review-text.review-text-content") %>%
  html_text()

reviewscom_5 <- comrev_5[1:13]
reviewscom_5 <- gsub("\n", "", reviewscom5)
reviewscom_5

framedf_5 <- data.frame(
  Name = namee_5, 
  Date = datereview_5, 
  Individual_Rating = indivrate_5, 
  Review = reviewscom_5
)
framedf_5

frame_df5 <- bind_rows(framedf5,framedf_5)
frame_df5

write.csv(frame_df5,"ProductsReviews5.csv")
read.csv("ProductsReviews5.csv")
```
SIXTH
```{r}
#6th product

library(polite)

url_6 <- "https://www.amazon.com.au/product-reviews/B0BC2C71H1/ref=cm_cr_arp_d_viewopt_rvwer/358-8254970-8794523?pd_rd_w=KeGty&content-id=amzn1.sym.26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_p=26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_r=P3F3GQJHZ7WCD2Y0ZGF2&pd_rd_wg=Wek4F&pd_rd_r=62d0ea19-08ae-4795-b3f8-c2bbeaf43ea9&pd_rd_i=B0BC2C71H1&reviewerType=avp_only_reviews&pageNumber=1"

session6<- bow(url_6, user_agent = "Educational Purposes")
session6

session6 <- session("https://www.amazon.com.au/product-reviews/B0BC2C71H1/ref=cm_cr_arp_d_viewopt_rvwer/358-8254970-8794523?pd_rd_w=KeGty&content-id=amzn1.sym.26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_p=26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_r=P3F3GQJHZ7WCD2Y0ZGF2&pd_rd_wg=Wek4F&pd_rd_r=62d0ea19-08ae-4795-b3f8-c2bbeaf43ea9&pd_rd_i=B0BC2C71H1&reviewerType=avp_only_reviews&pageNumber=1")

#Name of reviewer
namereview6 <- session6 %>%
  html_nodes("span.a-profile-name") %>%
  html_text()

namee6 <- namereview6 [1:12]
namee6

#Date of review
date6<- session6 %>%
  html_nodes("span.review-date") %>%
  html_text()

datereview6 <- date6[1:12]
datereview6

#Individual rating
rates6 <- session6 %>%
  html_nodes("span.a-icon-alt") %>%
  html_text()

indivrate6 <- rates6[1:12]
indivrate6

#Review comment 
comrev6 <- session6 %>%
  html_nodes("span.a-size-base.review-text.review-text-content") %>%
  html_text()

reviewscom6 <- comrev6[1:12]
reviewscom6 <- gsub("\n", "", reviewscom6)
reviewscom6

framedf6 <- data.frame(
  Name = namee6, 
  Date = datereview6, 
  Individual_Rating = indivrate6, 
  Review = reviewscom6
)
framedf6
```

```{r}
product6 <- "https://www.amazon.com.au/product-reviews/B0BC2C71H1/ref=cm_cr_getr_d_paging_btm_next_3/358-8254970-8794523?pd_rd_w=KeGty&content-id=amzn1.sym.26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_p=26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_r=P3F3GQJHZ7WCD2Y0ZGF2&pd_rd_wg=Wek4F&pd_rd_r=62d0ea19-08ae-4795-b3f8-c2bbeaf43ea9&pd_rd_i=B0BC2C71H1&reviewerType=avp_only_reviews&pageNumber=3"

sessionn6 <- bow(product6, user_agent = "Educational Purposes")
sessionn6


sessionnn6 <- session("https://www.amazon.com.au/product-reviews/B084TNSDHN/ref=cm_cr_arp_d_viewopt_rvwer/358-8254970-8794523?pd_rd_w=KeGty&content-id=amzn1.sym.26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_p=26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_r=P3F3GQJHZ7WCD2Y0ZGF2&pd_rd_wg=Wek4F&pd_rd_r=62d0ea19-08ae-4795-b3f8-c2bbeaf43ea9&pd_rd_i=B084TNSDHN&filterByStar=five_star&pageNumber=1&formatType=current_format&reviewerType=all_reviews&sortBy=helpful")

#Name of reviewer
namereview_6 <- sessionnn6 %>%
  html_nodes("span.a-profile-name") %>%
  html_text()

namee_6 <- namereview_6[1:13]
namee_6

#Date of review
date_6<- sessionnn6 %>%
  html_nodes("span.review-date") %>%
  html_text()

datereview_6 <- date_6[1:13]
datereview_6

#Individual rating
rates_6 <- sessionnn6 %>%
  html_nodes("span.a-icon-alt") %>%
  html_text()

indivrate_6 <- rates_6[1:13]
indivrate_6

#Review comment 
comrev_6 <- sessionnn6 %>%
  html_nodes("span.a-size-base.review-text.review-text-content") %>%
  html_text()

reviewscom_6 <- comrev_6[1:13]
reviewscom_6 <- gsub("\n", "", reviewscom_6)
reviewscom_6

framedf_6 <- data.frame(
  Name = namee_6, 
  Date = datereview_6, 
  Individual_Rating = indivrate_6, 
  Review = reviewscom_6 
)
framedf_6

frame_df6 <- bind_rows(framedf6,framedf_6)
frame_df6

write.csv(frame_df6,"ProductsReviews6.csv")
read.csv("ProductsReviews6.csv")

```
SEVEN
```{r}
#7th product 

url_7 <- "https://www.amazon.com.au/product-reviews/B084TNSDHN/ref=cm_cr_arp_d_viewopt_srt/358-8254970-8794523?pd_rd_w=KeGty&content-id=amzn1.sym.26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_p=26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_r=P3F3GQJHZ7WCD2Y0ZGF2&pd_rd_wg=Wek4F&pd_rd_r=62d0ea19-08ae-4795-b3f8-c2bbeaf43ea9&pd_rd_i=B084TNSDHN&filterByStar=four_star&pageNumber=1&formatType=current_format&reviewerType=avp_only_reviews&sortBy=recent"

session7 <- bow(url_7, user_agent = "Educational Purposes")
session7


library(rvest)
library(stringr)
library(httr2)
library(httr) 


session7 <- session("https://www.amazon.com.au/product-reviews/B084TNSDHN/ref=cm_cr_arp_d_viewopt_srt/358-8254970-8794523?pd_rd_w=KeGty&content-id=amzn1.sym.26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_p=26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_r=P3F3GQJHZ7WCD2Y0ZGF2&pd_rd_wg=Wek4F&pd_rd_r=62d0ea19-08ae-4795-b3f8-c2bbeaf43ea9&pd_rd_i=B084TNSDHN&filterByStar=four_star&pageNumber=1&formatType=current_format&reviewerType=avp_only_reviews&sortBy=recent")

#Name of reviewer
namereview7 <- session7 %>%
  html_nodes("span.a-profile-name") %>%
  html_text()

namee7 <- namereview7[1:13]
namee7

#Date of review
date7<- session7 %>%
  html_nodes("span.review-date") %>%
  html_text()

datereview7 <- date7[1:13]
datereview7

#Individual rating
rates7 <- session7 %>%
  html_nodes("span.a-icon-alt") %>%
  html_text()

indivrate7 <- rates7[1:13]
indivrate7

#Review comment 
comrev7 <- session7 %>%
  html_nodes("span.a-size-base.review-text.review-text-content") %>%
  html_text()

reviewscom7 <- comrev7[1:13]
reviewscom7 <- gsub("\n", "", reviewscom7)
reviewscom7

framedf7 <- data.frame(
  Name = namee7, 
  Date = datereview7, 
  Individual_Rating = indivrate7, 
  Review = reviewscom7 
)
framedf7
```
```{r}
urls7 <- "https://www.amazon.com.au/product-reviews/B084TNSDHN/ref=cm_cr_arp_d_viewopt_rvwer/358-8254970-8794523?pd_rd_w=KeGty&content-id=amzn1.sym.26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_p=26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_r=P3F3GQJHZ7WCD2Y0ZGF2&pd_rd_wg=Wek4F&pd_rd_r=62d0ea19-08ae-4795-b3f8-c2bbeaf43ea9&pd_rd_i=B084TNSDHN&filterByStar=five_star&pageNumber=1&formatType=current_format&reviewerType=all_reviews&sortBy=helpful"

sessionn7 <- bow(urls7, user_agent = "Educational Purposes")
sessionn7


sessionn7 <- session("https://www.amazon.com.au/product-reviews/B084TNSDHN/ref=cm_cr_arp_d_viewopt_rvwer/358-8254970-8794523?pd_rd_w=KeGty&content-id=amzn1.sym.26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_p=26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_r=P3F3GQJHZ7WCD2Y0ZGF2&pd_rd_wg=Wek4F&pd_rd_r=62d0ea19-08ae-4795-b3f8-c2bbeaf43ea9&pd_rd_i=B084TNSDHN&filterByStar=five_star&pageNumber=1&formatType=current_format&reviewerType=all_reviews&sortBy=helpful")

#Name of reviewer
namereview_7 <- sessionn7 %>%
  html_nodes("span.a-profile-name") %>%
  html_text()

namee_7 <- namereview_7 [1:12]
namee_7

#Date of review
date_7<- sessionn7 %>%
  html_nodes("span.review-date") %>%
  html_text()

datereview_7 <- date_7[1:12]
datereview_7

#Individual rating
rates_7 <- sessionn7 %>%
  html_nodes("span.a-icon-alt") %>%
  html_text()

indivrate_7 <- rates_7[1:12]
indivrate_7

#Review comment 
comrev_7 <- sessionn7 %>%
  html_nodes("span.a-size-base.review-text.review-text-content") %>%
  html_text()

reviewscom_7 <- comrev_7[1:12]
reviewscom_7 <- gsub("\n", "", reviewscom_7)
reviewscom_7

framedf_7 <- data.frame(
  Name = namee_7, 
  Date = datereview_7, 
  Individual_Rating = indivrate_7, 
  Review = reviewscom_7
)
framedf_7

frame_df7 <- bind_rows(framedf7,framedf_7)
frame_df7

write.csv(frame_df7,"ProductsReviews7.csv")
read.csv("ProductsReviews7.csv")
```
EIGHT---
```{r}
#8th product 

url_8 <- "https://www.amazon.com.au/product-reviews/B085G63QHT/ref=cm_cr_arp_d_viewopt_sr/358-8254970-8794523?pd_rd_w=nqMzK&content-id=amzn1.sym.26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_p=26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_r=MC2TYYP6DMVRAQZEWADY&pd_rd_wg=15aLU&pd_rd_r=c3604fac-49c7-4ff3-ab50-1c14e518d84d&pd_rd_i=B085G63QHT&filterByStar=critical&pageNumber=1"

session8 <- bow(url_8, user_agent = "Educational Purposes")
session8


library(rvest)
library(stringr)
library(httr2)
library(httr) 


session8 <- session("https://www.amazon.com.au/product-reviews/B085G63QHT/ref=cm_cr_arp_d_viewopt_sr/358-8254970-8794523?pd_rd_w=nqMzK&content-id=amzn1.sym.26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_p=26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_r=MC2TYYP6DMVRAQZEWADY&pd_rd_wg=15aLU&pd_rd_r=c3604fac-49c7-4ff3-ab50-1c14e518d84d&pd_rd_i=B085G63QHT&filterByStar=critical&pageNumber=1")

#Name of reviewer
namereview8 <- session8 %>%
  html_nodes("span.a-profile-name") %>%
  html_text()

namee8 <- namereview8 [1:12]
namee8

#Date of review
date8<- session8 %>%
  html_nodes("span.review-date") %>%
  html_text()

datereview8 <- date8[1:12]
datereview8

#Individual rating
rates8 <- session8 %>%
  html_nodes("span.a-icon-alt") %>%
  html_text()

indivrate8 <- rates8[1:12]
indivrate8

#Review comment 
comrev8 <- session8 %>%
  html_nodes("span.a-size-base.review-text.review-text-content") %>%
  html_text()

reviewscom8 <- comrev8[1:12]
reviewscom8 <- gsub("\n", "", reviewscom8)
reviewscom8

framedf8 <- data.frame(
  Name = namee8, 
  Date = datereview8, 
  Individual_Rating = indivrate8, 
  Review = reviewscom8
)
framedf8


urls8 <- "https://www.amazon.com.au/product-reviews/B085G63QHT/ref=cm_cr_arp_d_viewopt_sr/358-8254970-8794523?pd_rd_w=nqMzK&content-id=amzn1.sym.26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_p=26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_r=MC2TYYP6DMVRAQZEWADY&pd_rd_wg=15aLU&pd_rd_r=c3604fac-49c7-4ff3-ab50-1c14e518d84d&pd_rd_i=B085G63QHT&filterByStar=positive&pageNumber=1"

sessionn8 <- bow(urls8, user_agent = "Educational Purposes")
sessionn8


library(rvest)
library(stringr)
library(httr2)
library(httr) 


sessionn8 <- session("https://www.amazon.com.au/product-reviews/B085G63QHT/ref=cm_cr_arp_d_viewopt_sr/358-8254970-8794523?pd_rd_w=nqMzK&content-id=amzn1.sym.26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_p=26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_r=MC2TYYP6DMVRAQZEWADY&pd_rd_wg=15aLU&pd_rd_r=c3604fac-49c7-4ff3-ab50-1c14e518d84d&pd_rd_i=B085G63QHT&filterByStar=positive&pageNumber=1")

#Name of reviewer
namereview_8 <- sessionn8 %>%
  html_nodes("span.a-profile-name") %>%
  html_text()

namee_8 <- namereview_8[1:13]
namee_8

#Date of review
date_8<- sessionn8 %>%
  html_nodes("span.review-date") %>%
  html_text()

datereview_8 <- date_8[1:13]
datereview_8

#Individual rating
rates_8 <- sessionn8 %>%
  html_nodes("span.a-icon-alt") %>%
  html_text()

indivrate_8 <- rates_8[1:13]
indivrate_8

#Review comment 
comrev_8 <- sessionn8 %>%
  html_nodes("span.a-size-base.review-text.review-text-content") %>%
  html_text()

reviewscom_8 <- comrev_8[1:13]
reviewscom_8 <- gsub("\n", "", reviewscom_8)
reviewscom_8

framedf_8 <- data.frame(
  Name = namee_8, 
  Date = datereview_8, 
  Individual_Rating = indivrate_8, 
  Review = reviewscom_8 
)
framedf_8

frame_df8 <- bind_rows(framedf8,framedf_8)
frame_df8

write.csv(frame_df8,"ProductsReviews8.csv")
read.csv("ProductsReviews8.csv")
```

NINETH
```{r}
#9th product

url_9 <- "https://www.amazon.com.au/product-reviews/B085G63QHT/ref=cm_cr_arp_d_viewpnt_rgt/358-8254970-8794523?pd_rd_w=nqMzK&content-id=amzn1.sym.26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_p=26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_r=MC2TYYP6DMVRAQZEWADY&pd_rd_wg=15aLU&pd_rd_r=c3604fac-49c7-4ff3-ab50-1c14e518d84d&pd_rd_i=B085G63QHT&filterByStar=critical&pageNumber=1"

session9 <- bow(url_9, user_agent = "Educational Purposes")
session9


library(rvest)
library(stringr)
library(httr2)
library(httr) 


session9 <- session("https://www.amazon.com.au/product-reviews/B085G63QHT/ref=cm_cr_arp_d_viewpnt_rgt/358-8254970-8794523?pd_rd_w=nqMzK&content-id=amzn1.sym.26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_p=26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_r=MC2TYYP6DMVRAQZEWADY&pd_rd_wg=15aLU&pd_rd_r=c3604fac-49c7-4ff3-ab50-1c14e518d84d&pd_rd_i=B085G63QHT&filterByStar=critical&pageNumber=1")

#Name of reviewer
namereview9 <- session9 %>%
  html_nodes("span.a-profile-name") %>%
  html_text()

namee9 <- namereview9 [1:25]
namee9

#Date of review
date9<- session9 %>%
  html_nodes("span.review-date") %>%
  html_text()

datereview9 <- date9[1:25]
datereview9

#Individual rating
rates9 <- session9 %>%
  html_nodes("span.a-icon-alt") %>%
  html_text()

indivrate9 <- rates9[1:25]
indivrate9

#Review comment 
comrev9 <- session9 %>%
  html_nodes("span.a-size-base.review-text.review-text-content") %>%
  html_text()

reviewscom9 <- comrev9[1:25]
reviewscom9 <- gsub("\n", "", reviewscom9)
reviewscom9

framedf9 <- data.frame(
  Name = namee9, 
  Date = datereview9, 
  Individual_Rating = indivrate9, 
  Review = reviewscom9
)
framedf9

write.csv(framedf9,"ProductsReviews9.csv")
read.csv("ProductsReviews9.csv")
```

```
TENTH
```{r}
#10th product 

url10 <- "https://www.amazon.com.au/product-reviews/B09B8YP8KY/ref=cm_cr_arp_d_viewpnt_lft/358-8254970-8794523?pd_rd_w=H67GR&content-id=amzn1.sym.26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_p=26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_r=3AKYM9QPH4FPGV2WWTV0&pd_rd_wg=cTVuK&pd_rd_r=68ad7cf9-3866-41d7-92f8-5bd39efe3eba&pd_rd_i=B09B8YP8KY&filterByStar=positive&pageNumber=1"

session10 <- bow(url10, user_agent = "Educational Purposes")
session10

session10 <- session("https://www.amazon.com.au/product-reviews/B09B8YP8KY/ref=cm_cr_arp_d_viewpnt_lft/358-8254970-8794523?pd_rd_w=H67GR&content-id=amzn1.sym.26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_p=26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_r=3AKYM9QPH4FPGV2WWTV0&pd_rd_wg=cTVuK&pd_rd_r=68ad7cf9-3866-41d7-92f8-5bd39efe3eba&pd_rd_i=B09B8YP8KY&filterByStar=positive&pageNumber=1")

#Name of reviewer
namereview10 <- session10 %>%
  html_nodes("span.a-profile-name") %>%
  html_text()

namee10 <- namereview10 [1:25]
namee10

#Date of review
date10<- session10 %>%
  html_nodes("span.review-date") %>%
  html_text()

datereview10 <- date10[1:25]
datereview10

#Individual rating
rates10 <- session10 %>%
  html_nodes("span.a-icon-alt") %>%
  html_text()

indivrate10 <- rates10[1:25]
indivrate10

#Review comment 
comrev10 <- session10 %>%
  html_nodes("span.a-size-base.review-text.review-text-content") %>%
  html_text()

reviewscom10 <- comrev10[1:25]
reviewscom10 <- gsub("\n", "", reviewscom10)
reviewscom10

framedf10 <- data.frame(
  Name = namee10, 
  Date = datereview10, 
  Individual_Rating = indivrate10, 
  Review = reviewscom10
)
framedf10

write.csv(framedf10,"ProductsReviews10.csv")
read.csv("ProductsReviews10.csv")
```

ROWBIND

```{r} 

productsrev<- bind_rows(framedf1,
framedf2,
framedff3,
frame_df4,
frame_df5,
frame_df6,
frame_df7,
frame_df8,
framedf9,
framedf10)
productsrev
```
CSV

```{r} 


write.csv(productsrev, "250ProductsReviews.csv")

read.csv("250ProductsReviews.csv")

```





